---
title: "Counterfactual thought without counterfactual langauge"
author: "David Rose, Siying Zhang, Sophie Bridgers, Hyowon Gweon, Tobias Gerstenberg"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  bookdown::html_document2:
    toc: true
    toc_depth: 6
    toc_float: true
    theme: cosmo
    highlight: tango
---

# Load packages

```{r setup, include = F, message = F, warning = F}
library("xtable")         # for saving tables
library("emmeans")        # for comparing means
library("knitr")          # for knitting  
library("brms")           # for Bayesian data analysis
library("tinytable")      # for tidy tables
library("broom.mixed")    # for tidy model results
library("boot")           # for inv.logit() function
library("DT")             # for datatable() function 
library("RColorBrewer")   # for color palettes
library("Hmisc")          # for smean.cl.boot function
library("png")            # adding pngs to images
library("egg")            # for geom_custom
library("grid")           # functions for dealing with images 
library("magick")         # read in images 
library("patchwork")      # for combining plots
library("tidyverse")      # for everything else 
```

# Settings
```{r}
opts_chunk$set(echo = T, warning = F, message = F)

# Define a custom color palette
children_palette = brewer.pal(n = 9, name = "Greens")[-1]
adults_palette = "grey"
colors = c(children_palette, adults_palette)

# set theme 
theme_set(theme_classic())

# suppress grouping warning 
options(dplyr.summarise.inform = F)
```


# Helper functions

## Demographics for children
```{r}
print_demographics = function(data) {
  # gender
  data %>%
    group_by(gender) %>%
    summarise(n = n_distinct(participant)) %>%
    print()
  
  # age
  print('age:')
  mean(data$age, na.rm = T) %>% print()
  sd(data$age, na.rm = T) %>% print()
  
  # language spoken
 data %>%
    mutate(en_occurrence = ifelse(str_detect(lan_spoken, "en"), "en", "non-en")) %>%
    group_by(en_occurrence) %>%
    summarise(n = n_distinct(participant)) %>%
    print()

}

```


## Demographics for adults
```{r}
print_demographics_adults = function(data) {
  # gender
  data %>%
    group_by(gender) %>%
    summarise(n = n()) %>%
    print()
  
  # age
  print('age:')
  mean(data$age, na.rm = T) %>% print()
  sd(data$age, na.rm = T) %>% print()

# race
  data %>%
    group_by(race) %>%
    summarise(n = n()) %>%
    print()
  
}

```

# EXPERIMENT 1 
## CHILDREN
### DATA
#### Read in Data

```{r message=FALSE, warning=FALSE}

df.exp1_children = read_csv("../../data/experiment1/children/exp1_children.csv") %>%
  filter(row_number() >= 0 & row_number() <= 120) %>% 
  select(age, gender, lan_spoken, trial_1, trial_1_score, trial_2, trial_2_score, trial_3, trial_3_score, trial_4, trial_4_score, control_trial_score, total_score) %>%
  mutate(age_group = cut(age, breaks = c(3, 4, 5, 6, 7.1),
                         labels = c("3", "4", "5", "6"),
                         right = TRUE)) %>%
  # na.omit() %>%
  mutate(participant = 1:n(),
         total_score = as.numeric(total_score),
        across("trial_1"|"trial_2"|"trial_3"|"trial_4", ~case_when(
    grepl("(andy|emily)_correct_(left|right)_(andy|emily)", .) ~ "egg | basketball",
    grepl("(taylor|zoey)_correct_(left|right)_(taylor|zoey)", .) ~ "phone | rubberducky",
    grepl("(sara|leo)_correct_(left|right)_(sara|leo)", .) ~ "vase | toybear",
    grepl("(olivia|mason)_correct_(left|right)_(olivia|mason)", .) ~ "icecream | sunscreen",
    TRUE ~ .
  ))) %>%
  mutate(across(starts_with("trial"), as.character)) %>%
  pivot_longer(cols = c("trial_1", "trial_2", "trial_3", "trial_4"),
               names_to = "trial_order",
               values_to = "trial_name") %>%
  group_by(participant) %>%
  mutate(trial_score = case_when(
    trial_order == "trial_1" ~ trial_1_score,
    trial_order == "trial_2" ~ trial_2_score,
    trial_order == "trial_3" ~ trial_3_score,
    trial_order == "trial_4" ~ trial_4_score,
  )) %>%
  mutate(trial_score = as.numeric(trial_score),
         trial_order = str_replace(trial_order, "_", " ")) %>%
  select(participant, gender, lan_spoken, age, age_group, trial_order, trial_name, trial_score, total_score, control_trial_score) %>% 
  ungroup()
```

#### Demographics
```{r}

print_demographics(df.exp1_children)

```

### STATS
##### Bayesian Regression Models
###### Hypothesis 1 
```{r}

# Overall children will thank the individual who prevented the worse outcome from occurring at rates that exceed chance

fit.brm1 = brm(formula = trial_score ~ 1 + (1 | participant) + (1 | trial_name),
     data = df.exp1_children,
     family = "bernoulli", 
     cores = 4,
     file = "cache/brm1") 

fit.brm1 %>% 
  tidy(effects = c("fixed"),
       conf.int = TRUE,
       conf.level = 0.95,
       conf.method = "HPDinterval") %>% 
  mutate(across(.cols = c(estimate, conf.low, conf.high),
                .fns = ~ inv.logit(.))) %>% 
  select(estimate, contains("conf")) 
  

```

###### Hypothesis 2
```{r}

# The tendency to thank the individual who prevented the worse potential outcome from occurring will increase with age

fit.brm2 = brm(formula = trial_score ~ 1 + age + (1 | participant) + (1 | trial_name),
     data = df.exp1_children,
     family = "bernoulli", 
     cores = 4,
     file = "cache/brm2") 

fit.brm2 %>% 
  tidy(effects = c("fixed"),
       conf.int = TRUE,
       conf.level = 0.95,
       conf.method = "HPDinterval") %>% 
  filter(term == "age") %>%
  select(estimate, contains("conf"))
 
```

## ADULTS
### DATA
#### Read in data


```{r message=FALSE, warning=FALSE}

df.exp1_adults = read_csv("../../data/experiment1/adults/exp1_adults.csv")

```

#### Wrangle 

```{r}

df.exp1_adults = df.exp1_adults %>% 
  mutate(participant = 1:30) %>% 
  relocate(participant) %>% 
  select(-workerid:-post_test_trial, -error) %>% 
   pivot_longer(cols = c("video_1", "video_2", "video_3", "video_4"
   ),
   names_to = "video_version",
   values_to = "video"
  ) %>% 
  pivot_longer(cols = c("video_1_correct_answer", "video_2_correct_answer", "video_3_correct_answer", "video_4_correct_answer"),
               names_to = "video_version_correct_answer",
               values_to = "correct_answer") %>% 
  pivot_longer(cols = c("video_1_response", "video_2_response", "video_3_response", "video_4_response"),
                names_to = "video_version_response",
   values_to = "response") %>% 
  mutate(video_version_correct_answer = str_remove_all(video_version_correct_answer, "_correct_answer"),
         video_version_response = str_remove_all(video_version_response, "_response")) %>% 
  filter(video_version == video_version_correct_answer & video_version_correct_answer == video_version_response) %>% 
  select(participant, scenario = video, correct_answer, response) %>% 
  mutate(rating = if_else(correct_answer == response, 1, 0))

```

#### Demogrpahics

```{r}
# read in data
df.exp1_adults_demographics = read_csv("../../data/experiment1/adults/exp1_adults_demographics.csv")

# print demographics
print_demographics_adults(df.exp1_adults_demographics)


```

### STATS
#### Bayesian Regression Models
##### Hypothesis 1 
```{r}

# Overall adults will thank the individual who prevented the worse outcome from occurring at rates that exceed chance

# fit.brm1.adults = brm(formula = response ~ 1 + (1 | participant) + (1 | scenario),
#      data = df.exp1_adults,
#      family = "bernoulli",
#      cores = 4,
#      file = "cache/brm1.adults") 
# 
# fit.brm1.adults %>% 
#   tidy(effects = c("fixed"),
#        conf.int = TRUE,
#        conf.level = 0.95,
#        conf.method = "HPDinterval") %>% 
#   mutate(across(.cols = c(estimate, conf.low, conf.high),
#                 .fns = ~ inv.logit(.))) %>% 
#   select(estimate, contains("conf")) 
```


### PLOTS

#### Overall 

```{r fig.height=10, fig.width=8, message=FALSE, warning=FALSE}


# Load image as grob
overall_image <- readPNG("../../figures/experiment1/overall_still/experiment1.png")
overall_grob <- rasterGrob(overall_image, interpolate = TRUE, width = 1, vjust = 0, hjust = 0)

# Create a dataframe with the grob in a column named `image`
df.image = tibble(
  x = -Inf,
  y = Inf,
  image = list(overall_grob),
  facet_var = "Experiment 1"
)

# INDIVIDUAL DATA 

# children
df.exp1.children.individual = df.exp1_children %>%
  select(participant, age_group, age, total_score) %>% 
  distinct() %>% 
  mutate(pct_correct = total_score / 4) %>% 
  select(-total_score) %>% 
  mutate(facet_var = "Experiment 1")

# adults
df.exp1.adults.individual = df.exp1_adults %>%
  rename(trial_name = scenario) %>%
  group_by(participant) %>%
  summarise(
    total_score = sum(rating),
    pct_correct = mean(total_score) / 4) %>%
  ungroup() %>%
  mutate(age_group = "adults",
         age = 8) %>% 
  select(-total_score) %>% 
  mutate(facet_var = "Experiment 1")
  
# combine total counterfactual data for adults + children
df.combined.individual = bind_rows(df.exp1.children.individual,
                                   df.exp1.adults.individual)

# MEANS 
df.exp1.combinbed.means = df.combined.individual %>% 
  group_by(age_group) %>% 
  summarise(
    n = n(),
    age_mean = mean(age),
    response = smean.cl.boot(pct_correct)) %>%
  mutate(index = c("mean", "low", "high")) %>%
  ungroup() %>% 
  pivot_wider(names_from = index,
              values_from = response) %>% 
  mutate(facet_var = "Experiment 1")

# plot text showing n for adults + children
df.exp1.combined.text = df.exp1.combinbed.means %>% 
    select(age_group, age_mean, n) %>% 
    mutate(label = n,
           label = ifelse(age_group == "3", str_c("n = ", n), n),
           y = 0.95) %>% 
  mutate(facet_var = "Experiment 1")

p1 = ggplot() + 
  geom_hline(yintercept = seq(0, 1, 0.25),
             linetype = "dotted",
             alpha = 0.8) +
  geom_hline(yintercept = 0.5,
             linetype = "dashed") +
  geom_point(data = df.exp1.children.individual,
             mapping = aes(x = age,
                           y = pct_correct,
                           fill = age,
                           color = age),
             shape = 21,
             size = 2,
             color = "grey30",
             alpha = .4) +
  geom_pointrange(data = df.exp1.combinbed.means %>%
                    filter(age_group != "adults"),
                  mapping = aes(x = age_mean,
                                y = mean,
                                ymin = low,
                                ymax = high,
                                fill = age_mean),
                  shape = 21,
                  size = 1.5) +
  geom_pointrange(data = df.exp1.combinbed.means %>%
                    filter(age_group == "adults"),
                  mapping = aes(x = age_mean,
                                y = mean,
                                ymin = low,
                                ymax = high),
                  shape = 23,
                  fill = "grey",
                  size = 1.5) +
  geom_text(data = df.exp1.combined.text,
            mapping = aes(x = age_mean,
                          y = y,
                          label = label),
            size = 6.8,
            vjust = -1.8) +  
  geom_custom(data = df.image,
              mapping = aes(x = x, y = y, data = image),
              grob_fun = function(x) x) +
   facet_wrap(~facet_var,
              nrow = 1) +
  labs(y = "Percentage of choosing \n the person who prevented \n the worse outcome") +
  coord_cartesian(clip = "off",
                  ylim = c(0, 1)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = str_c(seq(0, 1, 0.25) * 100, "%"),
                     expand = expansion(add = c(0.05, 0.12))) + 
  scale_x_continuous(breaks = c(seq(3, 7, 1), 8),
                     labels = c(seq(3, 7, 1), "adult"), 
                     expand = expansion(add = c(0.2, 0.5))) +
  scale_fill_gradientn(colors = children_palette) + 
  scale_color_gradientn(colors = children_palette) + 
  labs(title = "A") +
  theme(axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title.y = element_text(size = 25),
        axis.title.x = element_blank(),
        strip.background = element_blank(),
        plot.title = element_text(size = 70,
                      face = "bold",
                      hjust = 0,
                      vjust = 22),
        strip.text = element_text(size = 36,
                                  vjust = 44.5,
                                  face = "bold"),
        legend.position = "none",
        plot.margin = margin(t = 12,
                             l = 0.5,
                             r = 0.5,
                             b = 0.5,
                             unit = "cm"))

# ggsave(filename = "../../figures/experiment1/exp1_results.pdf",
#        width = 8,
#        height = 10)


```

#### Per trial

```{r fig.width=24, fig.height=10, message=FALSE, warning=FALSE}
df.scenarios = tibble(short_name = c("egg_ball",
                                     "icecream_sunscreen",
                                     "vase_bear",
                                     "phone_duck"),
                        long_name = c("egg | basketball", 
                                      "icecream | sunscreen",
                                      "vase | toybear",
                                      "phone | rubberducky"))

# load trial images 
func_load_image = function(scenario){
  readPNG(str_c("../../figures/experiment1/trial_stills/", scenario, ".png"))
}

df.plot = df.exp1_children %>% 
  select(participant, age, age_group, scenario = trial_name, trial_score) %>% 
  bind_rows(df.exp1_adults %>% 
              select(participant, scenario, trial_score = rating) %>% 
              mutate(age_group = "adults",
                     age = 8) %>% 
              left_join(df.scenarios,
                        by = c("scenario" = "short_name")) %>% 
              select(-scenario) %>% 
              rename(scenario = long_name))

df.plot.means = df.plot %>% 
  group_by(age_group, scenario) %>% 
  summarise(
    n = n(),
    age_mean = mean(age),
    response = smean.cl.boot(trial_score)) %>%
  mutate(index = c("mean", "low", "high")) %>%
  ungroup() %>% 
  pivot_wider(names_from = index,
              values_from = response)
  

# plot text showing n for adults + children
df.exp1.combined.text = df.exp1.combinbed.means %>% 
    select(age_group, age_mean, n) %>% 
    mutate(label = n,
           label = ifelse(age_group == "3", str_c("n = ", n), n),
           y = 0.95)

# linking images and clips
df.images = df.plot %>% 
  select(scenario) %>% 
  distinct() %>% 
  mutate(grob = map(.x = scenario, .f = ~ func_load_image(scenario = .x)))

scenario_labels = as_labeller(
  c("egg | basketball" = "basketball | egg",
    "icecream | sunscreen" = "ice cream | sunscreen",
    "vase | toybear" = "bear | vase",
    "phone | rubberducky" = "phone | duck")
)

ggplot() + 
  geom_hline(yintercept = seq(0, 1, 0.25),
             linetype = "dotted",
             alpha = 0.8) +
  geom_hline(yintercept = 0.5,
             linetype = "dashed") +
  geom_pointrange(data = df.plot.means %>%
                    filter(age_group != "adults"),
                  mapping = aes(x = age_mean,
                                y = mean,
                                ymin = low,
                                ymax = high,
                                fill = age_mean),
                  shape = 21,
                  size = 1.5) +
  geom_pointrange(data = df.plot.means %>%
                    filter(age_group == "adults"),
                  mapping = aes(x = age_mean,
                                y = mean,
                                ymin = low,
                                ymax = high),
                  shape = 23,
                  fill = "grey",
                  size = 1.5) +
  geom_custom(data = df.images,
              mapping = aes(data = grob,
                            x = -Inf,
                            y = Inf),
              grob_fun = function(x) rasterGrob(x,
                                                interpolate = T,
                                                width = 1,
                                                vjust = 0,
                                                hjust = 0)) + 
 facet_wrap(~ scenario,
             nrow = 1,
             labeller = scenario_labels) +
  labs(x = "Age (in years)",
       y = "Percentage of choosing \n worse outcome prevented") +
  coord_cartesian(clip = "off",
                  ylim = c(0, 1)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = str_c(seq(0, 1, 0.25) * 100, "%"),
                     expand = expansion(add = c(0.05, 0.12))) + 
scale_x_continuous(
  breaks = c(3, 4, 5, 6, 7, 8),
  labels = c("3", "4", "5", "6", "7", "adult"),
  limits = c(3, 8), 
  expand = expansion(add = c(0, 0.5))  
) +
  scale_fill_gradientn(colors = children_palette) + 
  scale_color_gradientn(colors = children_palette) + 
  theme(axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title = element_text(size = 25),
        axis.title.x = element_blank(),
        strip.background = element_blank(),
        plot.title = element_blank(),
        panel.spacing.x = unit(2, units = "cm"),
        strip.text = element_text(size = 32,
                                  vjust = 39,
                                  face = "bold"),
        legend.position = "none",
        plot.margin = margin(t = 12,
                             l = 0.5,
                             r = 0.5,
                             b = 0.5,
                             unit = "cm"))

ggsave(filename = "../../figures/experiment1/exp1_results_trials.pdf",
       width = 24,
       height = 10)
```



# EXPERIMENT 2 

## CHILDREN

### DATA

#### Read in Data

```{r message=FALSE, warning=FALSE}

df.exp2_children = read_csv("../../data/experiment2/children/exp2_children.csv") %>%
  filter(row_number() >= 0 & row_number() <= 120) %>% 
  select(age, gender, lan_spoken, trial_1, trial_1_score, trial_2, trial_2_score, trial_3, trial_3_score, trial_4, trial_4_score, trial_5, trial_5_score, trial_6, trial_6_score, total_score) %>%
  mutate(age_group = cut(age, breaks = c(3, 4, 5, 6, 7.1),
                         labels = c("3", "4", "5", "6"),
                         right = TRUE)) %>%
  na.omit() %>%
  mutate(participant = 1:n(),
         total_score = as.numeric(total_score),
        across("trial_1"|"trial_2"|"trial_3"|"trial_4"|"trial_5"|"trial_6", ~case_when(
    grepl("lightbulb_laundry_correct_(left|right)_(jessie|caleb)", .) ~ "lightbulb",
    grepl("apple_trashcan_correct_(left|right)_(lily|alex)", .) ~ "apple",
    grepl("basketball_egg_correct_(left|right)_(charlie|noah)", .) ~ "basketball",
    grepl("glass_beanbag_correct_(left|right)_(emily|lucas)", .) ~ "glass",
    grepl("rock_wine_correct_(left|right)_(amber|billy)", .) ~ "rock",
    grepl("bear_water_correct_(left|right)_(vicky|connor)", .) ~ "bear",
    TRUE ~ .
  ))) %>%
  mutate(across(starts_with("trial"), as.character)) %>%
  pivot_longer(cols = c("trial_1", "trial_2", "trial_3", "trial_4", "trial_5", "trial_6"),
               names_to = "trial_order",
               values_to = "trial_name") %>%
  group_by(participant) %>%
  mutate(trial_score = case_when(
    trial_order == "trial_1" ~ trial_1_score,
    trial_order == "trial_2" ~ trial_2_score,
    trial_order == "trial_3" ~ trial_3_score,
    trial_order == "trial_4" ~ trial_4_score,
    trial_order == "trial_5" ~ trial_5_score,
    trial_order == "trial_6" ~ trial_6_score,
  )) %>%
  mutate(trial_score = as.numeric(trial_score)) %>%
  mutate(trial_order = ifelse(trial_order == "trial_1", "trial 1",
                               ifelse(trial_order == "trial_2", "trial 2",
                                      ifelse(trial_order == "trial_3", "trial 3",
                                             ifelse(trial_order == "trial_4", "trial 4",
                                                    ifelse(trial_order == "trial_5", "trial 5",
                                                           ifelse(trial_order == "trial_6", "trial 6", trial_order))))))) %>%
  mutate(side = case_when(
    trial_name %in% c("basketball", "bear", "apple", "rock") ~ "side with things",
    trial_name %in% c("lightbulb", "glass") ~ "side with nothing",
    TRUE ~ "Uncategorized" 
  )) %>%
  mutate(prefer_things = case_when(
    side == "side with things" & trial_score == 1 ~ 1,
    side == "side with nothing" & trial_score == 0 ~ 1,
    TRUE ~ 0
  )) %>%
  select(participant, gender, lan_spoken, age, age_group, trial_order, trial_name, trial_score, side, prefer_things, total_score)

```

#### Demographics

```{r}
print_demographics(df.exp2_children)
```

### STATS

#### Bayesian Regression Models

##### Hypothesis 1 

```{r message=FALSE, warning=FALSE}

# Overall children will thank the individual who prevented the worse outcome from occurring at rates that exceed chance

fit.brm3 = brm(formula = trial_score ~ 1 + (1 | participant) + (1 | trial_name),
     data = df.exp2_children,
     family = "bernoulli", 
     cores = 4,
     file = "cache/brm3") 

fit.brm3 %>% 
  tidy(effects = c("fixed"),
       conf.int = TRUE,
       conf.level = 0.95,
       conf.method = "HPDinterval") %>% 
  mutate(across(.cols = c(estimate, conf.low, conf.high),
                .fns = ~ inv.logit(.))) %>% 
  select(estimate, contains("conf"))

```

##### Hypothesis 2
```{r message=FALSE, warning=FALSE}

# The tendency to thank the individual who prevented the worse potential outcome from occurring will increase with age

fit.brm4 = brm(formula = trial_score ~ 1 + age + (1 | participant) + (1 | trial_name),
     data = df.exp2_children,
     family = "bernoulli", 
     cores = 4,
     file = "cache/brm4") 

fit.brm4 %>% 
  tidy(effects = c("fixed"),
       conf.int = TRUE,
       conf.level = 0.95,
       conf.method = "HPDinterval") %>% 
  filter(term == "age") %>%
  select(estimate, contains("conf")) 

```

## ADULTS
### DATA
#### Read in Data

```{r message=FALSE, warning=FALSE}

# import raw data
df.exp2_adults = read_csv("../../data/experiment2/adults/exp2_adults.csv")

```

#### Wrangle
```{r}
df.exp2_adults = df.exp2_adults %>% 
  mutate(participant = 1:n()) %>% 
  relocate(participant) %>% 
  select(-workerid, -error) %>% 
   pivot_longer(cols = c("video_1", "video_2", "video_3", "video_4", "video_5", "video_6"
   ),
   names_to = "video_version",
   values_to = "video"
  ) %>% 
  pivot_longer(cols = c("video_1_correct_answer", "video_2_correct_answer", "video_3_correct_answer", "video_4_correct_answer", "video_5_correct_answer", "video_6_correct_answer"),
               names_to = "video_version_correct_answer",
               values_to = "correct_answer") %>% 
  pivot_longer(cols = c("video_1_response", "video_2_response", "video_3_response", "video_4_response", "video_5_response", "video_6_response"),
                names_to = "video_version_response",
   values_to = "response") %>% 
  mutate(video_version_correct_answer = str_remove_all(video_version_correct_answer, "_correct_answer"),
         video_version_response = str_remove_all(video_version_response, "_response")) %>% 
  filter(video_version == video_version_correct_answer & video_version_correct_answer == video_version_response) %>% 
  mutate(age = "Adult") %>%
  select(age, participant, scenario = video, correct_answer, response) %>% 
  mutate(rating = if_else(correct_answer == response, 1, 0)) %>%
  rename(trial_response = response,
         response = rating) 

  
```

#### Demographics
```{r message=FALSE, warning=FALSE}

df.exp2_adults_demographics = read_csv("../../data/experiment2/adults/exp2_adults_demographics.csv") 
 

print_demographics_adults(df.exp2_adults_demographics)

```

### STATS
#### Bayesian Regression Models
##### Hypothesis 1 
```{r}

# Overall adults will thank the individual who prevented the worse outcome from occurring at rates that exceed chance

fit.brm3.adults = brm(formula = response ~ 1 + (1 | participant) + (1 | scenario),
     data = df.exp2_adults ,
     family = "bernoulli",
     cores = 4,
     file = "cache/brm3.adults") 

fit.brm3.adults %>% 
  tidy(effects = c("fixed"),
       conf.int = TRUE,
       conf.level = 0.95,
       conf.method = "HPDinterval") %>% 
  mutate(across(.cols = c(estimate, conf.low, conf.high),
                .fns = ~ inv.logit(.))) %>% 
  select(estimate, contains("conf")) 

```

## PLOTS

#### Overall 

```{r fig.height=10, fig.width=6.65, message=FALSE, warning=FALSE}



# Load image as grob
overall_image <- readPNG("../../figures/experiment2/overall_still/experiment2.png")
overall_grob <- rasterGrob(overall_image, interpolate = TRUE, width = 1, vjust = 0, hjust = 0)

# Create a dataframe with the grob in a column named `image`
df.image = tibble(
  x = -Inf,
  y = Inf,
  image = list(overall_grob),
  facet_var = "Experiment 2"
)

# INDIVIDUAL DATA 

# children
df.exp2.children.individual = df.exp2_children %>%
  select(participant, age_group, age, total_score) %>% 
  distinct() %>% 
  mutate(pct_correct = total_score / 6) %>% 
  select(-total_score) %>% 
  mutate(facet_var = "Experiment 2")

# adults
df.exp2.adults.individual = df.exp2_adults %>%
  rename(trial_name = scenario) %>%
  group_by(participant) %>%
  summarise(
    total_score = sum(response),
    pct_correct = mean(total_score) / 6) %>%
  ungroup() %>%
  mutate(age_group = "adults",
         age = 8) %>% 
  select(-total_score) %>% 
  mutate(facet_var = "Experiment 2")
  
# combine total counterfactual data for adults + children
df.combined.individual = bind_rows(df.exp2.children.individual,
                                   df.exp2.adults.individual)

# MEANS 
df.exp2.combinbed.means = df.combined.individual %>% 
  group_by(age_group) %>% 
  summarise(
    n = n(),
    age_mean = mean(age),
    response = smean.cl.boot(pct_correct)) %>%
  mutate(index = c("mean", "low", "high")) %>%
  ungroup() %>% 
  pivot_wider(names_from = index,
              values_from = response) %>% 
  mutate(facet_var = "Experiment 2")

# plot text showing n for adults + children
df.exp2.combined.text = df.exp2.combinbed.means %>% 
    select(age_group, age_mean, n) %>% 
    mutate(label = n,
           # label = ifelse(age_group == "3", str_c("n = ", n), n),
           y = 0.95) %>% 
  mutate(facet_var = "Experiment 2")

p2 = ggplot() + 
   geom_hline(yintercept = seq(0, 1, 0.166),
             linetype = "dotted",
             color = "black",
             alpha = 0.8) +
  geom_hline(yintercept = 0.5,
             linetype = "dashed") +
  geom_point(data = df.exp2.children.individual,
             mapping = aes(x = age,
                           y = pct_correct,
                           fill = age,
                           color = age),
             shape = 21,
             size = 2,
             color = "grey30",
             alpha = .4) +
  geom_pointrange(data = df.exp2.combinbed.means %>%
                    filter(age_group != "adults"),
                  mapping = aes(x = age_mean,
                                y = mean,
                                ymin = low,
                                ymax = high,
                                fill = age_mean),
                  shape = 21,
                  size = 1.5) +
  geom_pointrange(data = df.exp2.combinbed.means %>%
                    filter(age_group == "adults"),
                  mapping = aes(x = age_mean,
                                y = mean,
                                ymin = low,
                                ymax = high),
                  shape = 23,
                  fill = "grey",
                  size = 1.5) +
  geom_text(data = df.exp2.combined.text,
            mapping = aes(x = age_mean,
                          y = y,
                          label = label),
            size = 6.8,
            vjust = -1.8) +  
geom_custom(data = df.image,
              mapping = aes(x = x, y = y, data = image),
              grob_fun = function(x) x) +
   facet_wrap(~facet_var,
              nrow = 1) +
  coord_cartesian(clip = "off",
                  ylim = c(0, 1)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = str_c(seq(0, 1, 0.25) * 100, "%"),
                     expand = expansion(add = c(0.05, 0.12))) + 
  scale_x_continuous(breaks = c(seq(3, 7, 1), 8),
                     labels = c(seq(3, 7, 1), "adult"), 
                     expand = expansion(add = c(0.2, 0.5))) +
  scale_fill_gradientn(colors = children_palette) + 
  scale_color_gradientn(colors = children_palette) + 
  labs(title = "B") +
  theme(axis.text.x = element_text(size = 25),
        axis.text.y = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        strip.background = element_blank(),
        plot.title = element_text(size = 70,
                      face = "bold",
                      hjust = 0,
                      vjust = 22),
        strip.text = element_text(size = 36,
                                  vjust = 44.5,
                                  face = "bold"),
        legend.position = "none",
        plot.margin = margin(t = 12,
                             l = 0.5,
                             r = 0.5,
                             b = 0.5,
                             unit = "cm"))

# ggsave(filename = "../../figures/experiment2/exp2_results.pdf",
#        width = 6.65,
#        height = 10)
```


#### Per trial

```{r fig.width=24, fig.height=10, message=FALSE, warning=FALSE}


df.scenarios = tibble(short_name = c("bear",
                                     "lightbulb",
                                     "glass",
                                     "basketball",
                                     "apple",
                                     "rock"))

# load trial images 
func_load_image = function(scenario){
  readPNG(str_c("../../figures/experiment2/trial_stills/", scenario, ".png"))
}

df.plot = df.exp2_children %>% 
  select(participant, age, age_group, scenario = trial_name, trial_score) %>% 
  bind_rows(df.exp2_adults %>% 
              select(participant, scenario, trial_score = response) %>% 
              mutate(age_group = "adults",
                     age = 8) %>% 
              left_join(df.scenarios,
                        by = c("scenario" = "short_name"))) %>% 
  ungroup()

df.plot.means = df.plot %>% 
  group_by(age_group, scenario) %>% 
  summarise(
    n = n(),
    age_mean = mean(age),
    response = smean.cl.boot(trial_score)) %>%
  mutate(index = c("mean", "low", "high")) %>%
  ungroup() %>% 
  pivot_wider(names_from = index,
              values_from = response)
  

# plot text showing n for adults + children
df.exp2.combined.text = df.exp2.combinbed.means %>% 
    select(age_group, age_mean, n) %>% 
    mutate(label = n,
           label = ifelse(age_group == "3", str_c("n = ", n), n),
           y = 0.95)

df.images = df.plot %>% 
  select(scenario) %>% 
  distinct() %>% 
  mutate(grob = map(.x = scenario, .f = ~ func_load_image(.x)))


scenario_labels = as_labeller(
  c("bear" = "bears & dirty water",
    "lightbulb" = "lightbulbs & laundry",
    "glass" = "glasses & pillow",
    "basketball" = "basketballs & eggs",
    "apple" = "apples & trash",
    "rock" = "rocks & glasses")
)

ggplot() + 
   geom_hline(yintercept = seq(0, 1, 0.25),
             linetype = "dotted",
             alpha = 0.8) +
  geom_hline(yintercept = 0.5,
             linetype = "dashed") +
  geom_pointrange(data = df.plot.means %>%
                    filter(age_group != "adults"),
                  mapping = aes(x = age_mean,
                                y = mean,
                                ymin = low,
                                ymax = high,
                                fill = age_mean),
                  shape = 21,
                  size = 1.5) +
  geom_pointrange(data = df.plot.means %>%
                    filter(age_group == "adults"),
                  mapping = aes(x = age_mean,
                                y = mean,
                                ymin = low,
                                ymax = high),
                  shape = 23,
                  fill = "grey",
                  size = 1.5) +
  geom_custom(data = df.images,
              mapping = aes(data = grob, x = -Inf, y = Inf),
              grob_fun = function(x) rasterGrob(x, interpolate = TRUE, width = 1, vjust = 0, hjust = 0)) +
 facet_wrap(~ scenario,
             nrow = 1,
             labeller = scenario_labels) +
  labs(x = "Age (in years)",
       y = "Percentage of choosing \n worse outcome prevented") +
  coord_cartesian(clip = "off",
                  ylim = c(0, 1)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = str_c(seq(0, 1, 0.25) * 100, "%"),
                     expand = expansion(add = c(0.05, 0.12))) + 
 scale_x_continuous(
  breaks = c(3, 4, 5, 6, 7, 8),
  labels = c("3", "4", "5", "6", "7", "adult"),
  limits = c(3, 8), 
  expand = expansion(add = c(0, 0.5))  
) +
  scale_fill_gradientn(colors = children_palette) + 
  scale_color_gradientn(colors = children_palette) + 
  theme(axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title = element_text(size = 25),
        axis.title.x = element_blank(),
        strip.background = element_blank(),
        plot.title = element_blank(),
        panel.spacing.x = unit(2, units = "cm"),
        strip.text = element_text(size = 34,
                                  vjust = 35,
                                  face = "bold"),
        legend.position = "none",
        plot.margin = margin(t = 12,
                             l = 0.5,
                             r = 0.5,
                             b = 0.5,
                             unit = "cm"))

ggsave(filename = "../../figures/experiment2/exp2_results_trials.pdf",
       width = 34,
       height = 10)
```


# EXPERIMENT 3
## CHILDREN
### DATA
#### Read in Data

```{r message=FALSE, warning=FALSE}
df.exp3_children = read_csv("../../data/experiment3/children/exp3_children.csv")%>%
  filter(row_number() >= 0 & row_number() <= 240) %>% 
  select(age, gender, lan_spoken, trial_1, trial_1_score, trial_2, trial_2_score, trial_3, trial_3_score, trial_4, trial_4_score, trial_5, trial_5_score, trial_6, trial_6_score, total_score) %>%
  mutate(age_group = cut(age, breaks = c(3, 4, 5, 6, 7, 8, 9, 10, 11.1),
                         labels = c("3", "4", "5", "6", "7", "8", "9", "10"),
                         right = TRUE)) %>%
  na.omit() %>%
  mutate(participant = 1:n(),
         total_score = as.numeric(total_score),
        across("trial_1"|"trial_2"|"trial_3"|"trial_4"|"trial_5"|"trial_6", ~case_when(
    grepl("exp7_bulb_laundry_correct_(left|right)_(jessie|caleb)", .) ~ "lightbulb",
    grepl("exp7_apple_trashcan_correct_(left|right)_(lily|alex)", .) ~ "apple",
    grepl("exp7_basketball_egg_correct_(left|right)_(charlie|noah)", .) ~ "basketball",
    grepl("exp7_glass_beanbag_correct_(left|right)_(emily|lucas)", .) ~ "glass",
    grepl("exp7_rock_wine_correct_(left|right)_(amber|billy)", .) ~ "rock",
    grepl("exp7_bear_water_correct_(left|right)_(vicky|connor)", .) ~ "bear",
    TRUE ~ .
  ))) %>%
  mutate(across(starts_with("trial"), as.character)) %>%
  pivot_longer(cols = c("trial_1", "trial_2", "trial_3", "trial_4", "trial_5", "trial_6"),
               names_to = "trial_order",
               values_to = "trial_name") %>%
  group_by(participant) %>%
  mutate(trial_score = case_when(
    trial_order == "trial_1" ~ trial_1_score,
    trial_order == "trial_2" ~ trial_2_score,
    trial_order == "trial_3" ~ trial_3_score,
    trial_order == "trial_4" ~ trial_4_score,
    trial_order == "trial_5" ~ trial_5_score,
    trial_order == "trial_6" ~ trial_6_score,
  )) %>%
  mutate(trial_score = as.numeric(trial_score)) %>%
  mutate(trial_order = ifelse(trial_order == "trial_1", "trial 1",
                               ifelse(trial_order == "trial_2", "trial 2",
                                      ifelse(trial_order == "trial_3", "trial 3",
                                             ifelse(trial_order == "trial_4", "trial 4",
                                                    ifelse(trial_order == "trial_5", "trial 5",
                                                           ifelse(trial_order == "trial_6", "trial 6", trial_order))))))) %>%
  mutate(side = case_when(
    trial_name %in% c("basketball", "bear", "apple", "rock") ~ "side with things",
    trial_name %in% c("lightbulb", "glass") ~ "side with nothing",
    TRUE ~ "Uncategorized" 
  )) %>%
  mutate(prefer_things = case_when(
    side == "side with things" & trial_score == 1 ~ 1,
    side == "side with nothing" & trial_score == 0 ~ 1,
    TRUE ~ 0
  )) %>%
  select(participant, gender, lan_spoken, age, age_group, trial_order, trial_name, trial_score, side, prefer_things, total_score)

```

## Demographics
```{r message=FALSE, warning=FALSE}

print_demographics(df.exp3_children)

```
# STATS
## Bayesian Regression Models
### Hypothesis 1 
```{r message=FALSE, warning=FALSE}

# Overall children will thank the individual who prevented the worse outcome from occurring at rates that exceed chance

fit.brm5.children = brm(formula = trial_score ~ 1 + (1 | participant) + (1 | trial_name),
     data = df.exp3_children,
     family = "bernoulli", 
     cores = 4,
     file = "cache/brm5_children") 

fit.brm5.children %>% 
  tidy(effects = c("fixed"),
       conf.int = TRUE,
       conf.level = 0.95,
       conf.method = "HPDinterval") %>% 
  mutate(across(.cols = c(estimate, conf.low, conf.high),
                .fns = ~ inv.logit(.))) %>% 
  select(estimate, contains("conf"))

```

### Hypothesis 2
```{r message=FALSE, warning=FALSE}

# The tendency to thank the individual who prevented the worse potential outcome from occurring will increase with age

fit.brm5.children.age = brm(formula = trial_score ~ 1 + age + (1 | participant) + (1 | trial_name),
     data = df.exp3_children,
     family = "bernoulli", 
     cores = 4,
     file = "cache/brm5_children_age") 

fit.brm5.children.age %>% 
  tidy(effects = c("fixed"),
       conf.int = TRUE,
       conf.level = 0.95,
       conf.method = "HPDinterval") %>% 
  filter(term == "age") %>%
  select(estimate, contains("conf")) 

```

## ADULTS
### DATA
#### Read in Data

```{r message=FALSE, warning=FALSE}


setwd("../../data/experiment3/adults")

file_names = list.files(pattern="*.csv")
file_names = file_names[!file_names %in% c("m6f0atxjkr_same_participant_as_lhjb5uy11r.csv")]
all_data = do.call(rbind, lapply(file_names, read.csv)) %>%
  distinct()

write.csv(all_data, "exp3_adult.csv", row.names = FALSE)

df.exp3_adults = read_csv("exp3_adult.csv")

```

#### Wrangle
```{r}
df.exp3_adults = df.exp3_adults %>% 
  mutate(participant = 1:n()) %>% 
  relocate(participant) %>% 
   pivot_longer(cols = c("video_1", "video_2", "video_3", "video_4", "video_5", "video_6"
   ),
   names_to = "video_version",
   values_to = "video"
  ) %>% 
  pivot_longer(cols = c("video_1_correct_answer", "video_2_correct_answer", "video_3_correct_answer", "video_4_correct_answer", "video_5_correct_answer", "video_6_correct_answer"),
               names_to = "video_version_correct_answer",
               values_to = "correct_answer") %>% 
  pivot_longer(cols = c("video_1_response", "video_2_response", "video_3_response", "video_4_response", "video_5_response", "video_6_response"),
                names_to = "video_version_response",
   values_to = "response") %>% 
  mutate(video_version_correct_answer = str_remove_all(video_version_correct_answer, "_correct_answer"),
         video_version_response = str_remove_all(video_version_response, "_response")) %>% 
  filter(video_version == video_version_correct_answer & video_version_correct_answer == video_version_response) %>% 
  mutate(age = "Adult") %>%
  select(age, participant, scenario = video, correct_answer, response, feedback) %>% 
  mutate(rating = if_else(correct_answer == response, 1, 0)) %>%
  rename(trial_response = response,
         response = rating) 

```


#### Demographics
```{r message=FALSE, warning=FALSE}

# read in data
df.exp3_adults_demographics = read_csv("../../data/experiment3/adults/exp3_adult.csv")

# print demographics
print_demographics_adults(df.exp3_adults_demographics)

```

### STATS
#### Bayesian Regression Models
##### Hypothesis 1 
```{r message=FALSE, warning=FALSE}

# Overall adults will thank the individual who prevented the worse outcome from occurring at rates that exceed chance

fit.brm5.adults = brm(formula = response ~ 1 + (1 | participant) + (1 | scenario),
     data = df.exp3_adults,
     family = "bernoulli",
     cores = 4,
     file = "cache/brm5.adults") 

fit.brm5.adults %>% 
  tidy(effects = c("fixed"),
       conf.int = TRUE,
       conf.level = 0.95,
       conf.method = "HPDinterval") %>% 
  mutate(across(.cols = c(estimate, conf.low, conf.high),
                .fns = ~ inv.logit(.))) %>% 
  select(estimate, contains("conf")) 

```
## PLOTS

#### Overall

```{r fig.height=10, fig.width=6.7, message=FALSE, warning=FALSE}

# Load image as grob
overall_image <- readPNG("../../figures/experiment3/overall_still/experiment3.png")
overall_grob <- rasterGrob(overall_image, interpolate = TRUE, width = 1, vjust = 0, hjust = 0)

# Create a dataframe with the grob in a column named `image`
df.image = tibble(
  x = -Inf,
  y = Inf,
  image = list(overall_grob),
  facet_var = "Experiment 3"
)


# INDIVIDUAL DATA 

# children
df.exp3.children.individual = df.exp3_children %>%
  select(participant, age_group, age, total_score) %>% 
  distinct() %>% 
  mutate(pct_correct = total_score / 6) %>% 
  select(-total_score) %>% 
  mutate(facet_var = "Experiment 3")

# adults
df.exp3.adults.individual = df.exp3_adults %>%
  rename(trial_name = scenario) %>%
  group_by(participant) %>%
  summarise(
    total_score = sum(response),
    pct_correct = mean(total_score) / 6) %>%
  ungroup() %>%
  mutate(age_group = "adults",
         age = 12) %>% 
  select(-total_score) %>% 
  mutate(facet_var = "Experiment 3")
  
# combine total counterfactual data for adults + children
df.combined.individual = bind_rows(df.exp3.children.individual,
                                   df.exp3.adults.individual)

# MEANS 
df.exp3.combinbed.means = df.combined.individual %>% 
  group_by(age_group) %>% 
  summarise(
    n = n(),
    age_mean = mean(age),
    response = smean.cl.boot(pct_correct)) %>%
  mutate(index = c("mean", "low", "high")) %>%
  ungroup() %>% 
  pivot_wider(names_from = index,
              values_from = response) %>% 
  mutate(facet_var = "Experiment 3")

# plot text showing n for adults + children
df.exp3.combined.text = df.exp3.combinbed.means %>% 
    select(age_group, age_mean, n) %>% 
    mutate(label = n,
           # label = ifelse(age_group == "3", str_c("n = ", n), n),
           y = 0.95) %>% 
  mutate(facet_var = "Experiment 3")

p3 = ggplot() + 
   geom_hline(yintercept = seq(0, 1, 0.166),
             linetype = "dotted",
             color = "black",
             alpha = 0.8) +
  geom_hline(yintercept = 0.5,
             linetype = "dashed") +
  geom_point(data = df.exp3.children.individual,
             mapping = aes(x = age,
                           y = pct_correct,
                           fill = age,
                           color = age),
             shape = 21,
             size = 2,
             color = "grey30",
             alpha = .4) +
  geom_pointrange(data = df.exp3.combinbed.means %>%
                    filter(age_group != "adults"),
                  mapping = aes(x = age_mean,
                                y = mean,
                                ymin = low,
                                ymax = high,
                                fill = age_mean),
                  shape = 21,
                  size = 1.5) +
  geom_pointrange(data = df.exp3.combinbed.means %>%
                    filter(age_group == "adults"),
                  mapping = aes(x = age_mean,
                                y = mean,
                                ymin = low,
                                ymax = high),
                  shape = 23,
                  fill = "grey",
                  size = 1.5) +
  geom_text(data = df.exp3.combined.text,
            mapping = aes(x = age_mean,
                          y = y,
                          label = label),
            size = 6.8,
            vjust = -1.8) +  
  geom_custom(data = df.image,
              mapping = aes(x = x, y = y, data = image),
              grob_fun = function(x) x) +
   facet_wrap(~facet_var,
              nrow = 1) +
  coord_cartesian(clip = "off",
                  ylim = c(0, 1)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = str_c(seq(0, 1, 0.25) * 100, "%"),
                     expand = expansion(add = c(0.05, 0.12))) + 
  scale_x_continuous(breaks = c(seq(3, 11, 1), 12),
                     labels = c(seq(3, 11, 1), "adult"), 
                     expand = expansion(add = c(0.2, 0.5))) +
  scale_fill_gradientn(colors = children_palette) + 
  scale_color_gradientn(colors = children_palette) + 
  labs(title = "C") +
  theme(axis.text.x = element_text(size = 25),
        axis.text.y = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        strip.background = element_blank(),
        plot.title = element_text(size = 70,
                      face = "bold",
                      hjust = 0,
                      vjust = 22),
        strip.text = element_text(size = 36,
                                  vjust = 44.5,
                                  face = "bold"),
        legend.position = "none",
        plot.margin = margin(t = 12,
                             l = 0.5,
                             r = 0.5,
                             b = 0.5,
                             unit = "cm"))


# ggsave(filename = "../../figures/experiment3/exp3_results.pdf",
#        width = 6.7,
#        height = 10)
```



#### Per trial

```{r fig.width=24, fig.height=10, message=FALSE, warning=FALSE}


df.scenarios = tibble(short_name = c("bear",
                                     "lightbulb",
                                     "glass",
                                     "basketball",
                                     "apple",
                                     "rock"))

# load trial images 
func_load_image = function(scenario){
  readPNG(str_c("../../figures/experiment3/trial_stills/", scenario, ".png"))
}

df.plot = df.exp3_children %>% 
  select(participant, age, age_group, scenario = trial_name, trial_score) %>% 
  bind_rows(df.exp3_adults %>% 
              select(participant, scenario, trial_score = response) %>% 
              mutate(age_group = "adults",
                     age = 12) %>% 
              left_join(df.scenarios,
                        by = c("scenario" = "short_name"))) %>% 
  ungroup()

df.plot.means = df.plot %>% 
  group_by(age_group, scenario) %>% 
  summarise(
    n = n(),
    age_mean = mean(age),
    response = smean.cl.boot(trial_score)) %>%
  mutate(index = c("mean", "low", "high")) %>%
  ungroup() %>% 
  pivot_wider(names_from = index,
              values_from = response)
  

# plot text showing n for adults + children
df.exp3.combined.text = df.exp3.combinbed.means %>% 
    select(age_group, age_mean, n) %>% 
    mutate(label = n,
           label = ifelse(age_group == "3", str_c("n = ", n), n),
           y = 0.95)

df.images = df.plot %>% 
  select(scenario) %>% 
  distinct() %>% 
  mutate(grob = map(.x = scenario, .f = ~ func_load_image(.x)))


scenario_labels = as_labeller(
  c("bear" = "bears & dirty water",
    "lightbulb" = "lightbulbs & laundry",
    "glass" = "glasses & pillow",
    "basketball" = "basketballs & eggs",
    "apple" = "apples & trash",
    "rock" = "rocks & glasses")
)

ggplot() + 
   geom_hline(yintercept = seq(0, 1, 0.25),
             linetype = "dotted",
             alpha = 0.8) +
  geom_hline(yintercept = 0.5,
             linetype = "dashed") +
  geom_pointrange(data = df.plot.means %>%
                    filter(age_group != "adults"),
                  mapping = aes(x = age_mean,
                                y = mean,
                                ymin = low,
                                ymax = high,
                                fill = age_mean),
                  shape = 21,
                  size = 1.5) +
  geom_pointrange(data = df.plot.means %>%
                    filter(age_group == "adults"),
                  mapping = aes(x = age_mean,
                                y = mean,
                                ymin = low,
                                ymax = high),
                  shape = 23,
                  fill = "grey",
                  size = 1.5) +
  geom_custom(data = df.images,
              mapping = aes(data = grob, x = -Inf, y = Inf),
              grob_fun = function(x) rasterGrob(x, interpolate = TRUE, width = 1, vjust = 0, hjust = 0)) +
 facet_wrap(~ scenario,
             nrow = 1,
             labeller = scenario_labels) +
  labs(x = "Age (in years)",
       y = "Percentage of choosing \n worse outcome prevented") +
  coord_cartesian(clip = "off",
                  ylim = c(0, 1)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = str_c(seq(0, 1, 0.25) * 100, "%"),
                     expand = expansion(add = c(0.05, 0.12))) + 
 scale_x_continuous(
  breaks = c(3, 4, 5, 6, 7, 8, 9, 10, 11, 12),
  labels = c("3", "4", "5", "6", "7", "8", "9", "10", "11", "adult"),
  limits = c(3, 12), 
  expand = expansion(add = c(0, 0.5))  
) +
  scale_fill_gradientn(colors = children_palette) + 
  scale_color_gradientn(colors = children_palette) + 
  theme(axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title = element_text(size = 25),
        axis.title.x = element_blank(),
        strip.background = element_blank(),
        plot.title = element_blank(),
        panel.spacing.x = unit(2, units = "cm"),
        strip.text = element_text(size = 45,
                                  vjust = 36,
                                  face = "bold"),
        legend.position = "none",
        plot.margin = margin(t = 12,
                             l = 0.5,
                             r = 0.5,
                             b = 0.5,
                             unit = "cm"))

ggsave(filename = "../../figures/experiment3/exp3_results_trials.pdf",
       width = 44,
       height = 10)
```


# PLOTS
## Overall Experiment Plots Combined

```{r fig.height=10, fig.width=20, message=FALSE, warning=FALSE}

# Combine the plots horizontally
combined_plot = p1 + p2 + p3 + 
  plot_layout(ncol = 3) 

ggsave(filename = "../../figures/overall_results.pdf",
       width = 22,
       height = 12)


```


# SESSION INFO

```{r}
sessionInfo()
```