---
title: "Probing counterfactual thinking without counterfactual langauge"
author: "David Rose, Siying Zhang, Sophie Bridgers, Hyowon Gweon, Tobias Gerstenberg"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  bookdown::html_document2:
    toc: true
    toc_depth: 6
    toc_float: true
    theme: cosmo
    highlight: tango
---

# Load packages
```{r message = F, warning = F}

library("xtable")         # for saving tables
library("emmeans")        # for comparing means
library("knitr")          # for knitting  
library("brms")           # for Bayesian data analysis
library("tinytable")      # for tidy tables
library("broom.mixed")    # for tidy model results
library("boot")           # for inv.logit() function
library("DT")             # for datatable() function 
library("RColorBrewer")   # for color palettes
library("Hmisc")          # for smean.cl.boot function
library("png")            # adding pngs to images
library("egg")            # for geom_custom
library("grid")           # functions for dealing with images 
library("magick")         # read in images 
library("patchwork")      # for combining plots
library("tidyverse")      # for everything else 

```

# Settings
```{r}

# suppress warnings and messages
opts_chunk$set(warning = FALSE, message = FALSE) 

# define a custom color palette
children_palette = brewer.pal(n = 9, name = "Greens")[-1]
adults_palette = "grey"
colors = c(children_palette, adults_palette)

# set theme 
theme_set(theme_classic())

# suppress grouping warning 
options(dplyr.summarise.inform = F)

```

# Helper functions

## Demographics for children
```{r}

print_demographics = function(data) {
  # gender
  data %>%
    group_by(gender) %>%
    summarise(n = n_distinct(participant)) %>%
    print()
  
  # age
  print('age:')
  mean(data$age, na.rm = T) %>% print()
  sd(data$age, na.rm = T) %>% print()
  
  # language spoken
  data %>%
    mutate(en_occurrence = ifelse(str_detect(lan_spoken, "en"), 
                                  "en", "non-en")) %>%
    group_by(en_occurrence) %>%
    summarise(n = n_distinct(participant)) %>%
    print()
}

```

## Demographics for adults
```{r}

print_demographics_adults = function(data) {
  # gender
  data %>%
    group_by(gender) %>%
    summarise(n = n()) %>%
    print()
  
  # age
  print('age:')
  mean(data$age, na.rm = T) %>% print()
  sd(data$age, na.rm = T) %>% print()
  
  # race
  data %>%
    group_by(race) %>%
    summarise(n = n()) %>%
    print()
}

```

## Plotting function for above chance performance 
```{r}

fun_plot_above_chance = function(data, cross_age){
  ggplot(data = data,
         mapping = aes(x = age, 
                       y = mean)) +
    geom_ribbon(mapping = aes(ymin = lower,
                              ymax = upper), 
                alpha = 0.2, 
                fill = "darkgreen") +
    geom_line(color = "darkgreen",
              size = 1) +
    geom_hline(yintercept = 0.5,
               linetype = "dashed",
               color = "red") +
    geom_vline(xintercept = cross_age,
               linetype = "dotted",
               color = "blue") +
    annotate("text",
             x = cross_age,
             y = 0.52, 
             label = paste0("Crossing at age ≈ ", round(cross_age, 2)), 
             color = "blue",
             hjust = -0.1) +
    labs(x = "Age", 
         y = "Predicted Probability",
         title = "Predicted Success Across Age",
         subtitle = "Shaded area = 95% credible interval; red dashed = chance level") +
    theme_minimal(base_size = 14)
}

```


# EXPERIMENT 1 

## CHILDREN

### DATA

#### Read in Data
```{r}

df.exp1_children = read_csv("../../data/experiment1/children/exp1_children.csv", show_col_types = F) 

```

#### Wrangle

```{r}

df.exp1_children = df.exp1_children %>%
  filter(row_number() >= 0 & row_number() <= 120) %>% 
  select(age,
         gender,
         lan_spoken,
         trial_1,
         trial_1_score,
         trial_2,
         trial_2_score,
         trial_3,
         trial_3_score,
         trial_4,
         trial_4_score,
         control_trial_score,
         total_score) %>%
  mutate(age_group = cut(age,
                         breaks = c(3, 4, 5, 6, 7.1),
                         labels = c("3", "4", "5", "6"),
                         right = TRUE)) %>%
  # na.omit() %>%
  mutate(participant = 1:n(),
         total_score = as.numeric(total_score),
         across(.cols = "trial_1"|"trial_2"|"trial_3"|"trial_4",
                .fns = ~case_when(
                  grepl("(andy|emily)_correct_(left|right)_(andy|emily)", .) ~ 
                    "egg | basketball",
                  grepl("(taylor|zoey)_correct_(left|right)_(taylor|zoey)", .) ~ 
                    "phone | rubberducky",
                  grepl("(sara|leo)_correct_(left|right)_(sara|leo)", .) ~ 
                    "vase | toybear",
                  grepl("(olivia|mason)_correct_(left|right)_(olivia|mason)", .) ~ 
                    "icecream | sunscreen",
                  TRUE ~ .
                ))) %>%
  mutate(across(starts_with("trial"), as.character)) %>%
  pivot_longer(cols = c("trial_1", 
                        "trial_2", 
                        "trial_3", 
                        "trial_4"),
               names_to = "trial_order",
               values_to = "trial_name") %>%
  group_by(participant) %>%
  mutate(trial_score = case_when(
    trial_order == "trial_1" ~ trial_1_score,
    trial_order == "trial_2" ~ trial_2_score,
    trial_order == "trial_3" ~ trial_3_score,
    trial_order == "trial_4" ~ trial_4_score,
  )) %>%
  mutate(trial_score = as.numeric(trial_score),
         trial_order = str_replace(trial_order, "_", " ")) %>%
  select(participant,
         gender,
         lan_spoken,
         age,
         age_group,
         trial_order,
         trial_name,
         trial_score,
         total_score,
         control_trial_score) %>% 
  ungroup()

```

#### Demographics
```{r}

print_demographics(df.exp1_children)

```

### STATS

#### Hypothesis 1 

Overall children will thank the individual who prevented the worse outcome from occurring at rates that exceed chance. 

```{r}

fit.brm1 = brm(formula = trial_score ~ 1 + (1 | participant) + (1 | trial_name),
               data = df.exp1_children,
               family = "bernoulli", 
               cores = 4,
               seed = 1,
               file = "cache/brm1") 

fit.brm1 %>% 
  tidy(effects = c("fixed"),
       conf.int = TRUE,
       conf.level = 0.95,
       conf.method = "HPDinterval") %>% 
  mutate(across(.cols = c(estimate, conf.low, conf.high),
                .fns = ~ inv.logit(.))) %>% 
  select(estimate, contains("conf")) 

```

#### Hypothesis 2

The tendency to thank the individual who prevented the worse potential outcome from occurring will increase with age. 

```{r}

fit.brm2 = brm(formula = trial_score ~ 1 + age + (1 | participant) + (1 | trial_name),
               data = df.exp1_children,
               family = "bernoulli", 
               cores = 4,
               file = "cache/brm2") 

fit.brm2 %>% 
  tidy(effects = c("fixed"),
       conf.int = TRUE,
       conf.level = 0.95,
       conf.method = "HPDinterval") %>% 
  filter(term == "age") %>%
  select(estimate, contains("conf"))

```

#### Above chance performance 
```{r}

# At what age will children perform above chance?

df.exp1_age_grid = tibble(age = seq(min(df.exp1_children$age),
                                    max(df.exp1_children$age),
                                    length.out = 200))

# Get posterior draws of predicted probabilities
preds = posterior_epred(fit.brm2,
                        newdata = df.exp1_age_grid,
                        re_formula = NA)

df.exp1.age.min = as_tibble(t(preds)) %>%
  mutate(age = df.exp1_age_grid$age) %>%
  pivot_longer(-age,
               names_to = "draw",
               values_to = "p") %>%
  group_by(age) %>%
  summarise(mean = mean(p),
            lower = quantile(p, 0.025),
            upper = quantile(p, 0.975),
            .groups = "drop")

cross_age = df.exp1.age.min %>%
  filter(lower > 0.5) %>%
  summarise(min_age = min(age)) %>%
  pull(min_age)

fun_plot_above_chance(data = df.exp1.age.min,
                    cross_age = cross_age)

```

## ADULTS

### DATA

#### Read in data
```{r}

df.exp1_adults = read_csv("../../data/experiment1/adults/exp1_adults.csv", show_col_types = F)

```

#### Wrangle 
```{r}

df.exp1_adults = df.exp1_adults %>% 
  mutate(participant = 1:30) %>% 
  relocate(participant) %>% 
  select(-workerid:-post_test_trial, 
         -error) %>% 
  pivot_longer(cols = c("video_1", "video_2", "video_3", "video_4"),
  names_to = "video_version",
  values_to = "video") %>% 
  pivot_longer(cols = c("video_1_correct_answer",
                        "video_2_correct_answer",
                        "video_3_correct_answer",
                        "video_4_correct_answer"),
               names_to = "video_version_correct_answer",
               values_to = "correct_answer") %>% 
  pivot_longer(cols = c("video_1_response",
                        "video_2_response",
                        "video_3_response",
                        "video_4_response"),
               names_to = "video_version_response",
               values_to = "response") %>% 
  mutate(video_version_correct_answer = str_remove_all(video_version_correct_answer,
                                                       "_correct_answer"),
         video_version_response = str_remove_all(video_version_response,
                                                 "_response")) %>% 
  filter((video_version == video_version_correct_answer) & 
           (video_version_correct_answer == video_version_response)) %>% 
  select(participant,
         scenario = video,
         correct_answer,
         response) %>% 
  mutate(rating = if_else(correct_answer == response, 1, 0))

```

#### Demographics
```{r}

# read in data
df.exp1_adults_demographics = read_csv("../../data/experiment1/adults/exp1_adults_demographics.csv", show_col_types = F)

# print demographics
print_demographics_adults(df.exp1_adults_demographics)

```

### STATS

#### Hypothesis 1 

Overall, adults will thank the individual who prevented the worse outcome from occurring at rates that exceed chance.
NOTE: Adult performance was at 100%, so this model cannot be fitted. 

```{r eval=FALSE}

fit.brm1.adults = brm(formula = response ~ 1 + (1 | participant) + (1 | scenario),
     data = df.exp1_adults,
     family = "bernoulli",
     cores = 4,
     file = "cache/brm1.adults")

fit.brm1.adults %>%
  tidy(effects = c("fixed"),
       conf.int = TRUE,
       conf.level = 0.95,
       conf.method = "HPDinterval") %>%
  mutate(across(.cols = c(estimate, conf.low, conf.high),
                .fns = ~ inv.logit(.))) %>%
  select(estimate, contains("conf"))

```

## PLOTS

### Overall 

```{r, fig.height=12, fig.width=7, warning=FALSE}

set.seed(1)

# Load image as grob
overall_image = readPNG("../../figures/experiment1/overall_still/experiment1.png")
overall_grob = rasterGrob(overall_image, 
                          interpolate = TRUE, 
                          width = 1, 
                          vjust = -0.1, 
                          hjust = 0)

# Create a dataframe with the grob in a column named `image`
df.image = tibble(x = -Inf,
                  y = Inf,
                  image = list(overall_grob))

# INDIVIDUAL DATA 

# children
df.exp1.children.individual = df.exp1_children %>%
  select(participant, 
         age_group, 
         age, 
         total_score) %>% 
  distinct() %>% 
  mutate(pct_correct = total_score / 4) %>% 
  select(-total_score)

# adults
df.exp1.adults.individual = df.exp1_adults %>%
  rename(trial_name = scenario) %>%
  group_by(participant) %>%
  summarise(total_score = sum(rating),
            pct_correct = total_score / 4) %>%
  ungroup() %>%
  mutate(age_group = "adults",
         age = 8) %>% 
  select(-total_score)

# combine total counterfactual data for adults + children
df.combined.individual = bind_rows(df.exp1.children.individual,
                                   df.exp1.adults.individual)

# MEANS 
df.exp1.combined.means = df.combined.individual %>% 
  group_by(age_group) %>% 
  summarise(n = n(),
            age_mean = mean(age),
            response = smean.cl.boot(pct_correct)) %>%
  mutate(index = c("mean", "low", "high")) %>%
  ungroup() %>% 
  pivot_wider(names_from = index,
              values_from = response)

# plot text showing n for adults + children
# df.exp1.combined.text = df.exp1.combinbed.means %>% 
#   select(age_group, 
#          age_mean,
#          n) %>% 
#   mutate(label = n,
#          label = ifelse(age_group == "3", 
#                         str_c("n = ", n), 
#                         n),
#          y = 0.95)

p1 = ggplot() + 
  geom_hline(yintercept = seq(0, 1, 0.25),
             linetype = "solid",
             alpha = 0.1) +
  geom_hline(yintercept = 0.5,
             linetype = "dashed") +
  geom_ribbon(data = df.exp1.age.min,
              aes(x = age, 
                  ymin = lower, 
                  ymax = upper),
              inherit.aes = FALSE,
              alpha = 0.2, 
              fill = "darkgreen") +
  geom_line(data = df.exp1.age.min,
            aes(x = age, 
                y = mean),
            inherit.aes = FALSE,
            color = "darkgreen", 
            size = 1) +
  geom_point(data = df.exp1.children.individual,
             mapping = aes(x = age,
                           y = pct_correct,
                           fill = age,
                           color = age),
             shape = 21,
             size = 2,
             color = "grey30",
             alpha = .4) +
  geom_pointrange(data = df.exp1.combined.means %>%
                    filter(age_group != "adults"),
                  mapping = aes(x = age_mean,
                                y = mean,
                                ymin = low,
                                ymax = high,
                                fill = age_mean),
                  shape = 21,
                  size = 1.5) +
  geom_pointrange(data = df.exp1.combined.means %>%
                    filter(age_group == "adults"),
                  mapping = aes(x = age_mean,
                                y = mean,
                                ymin = low,
                                ymax = high),
                  shape = 23,
                  fill = "grey",
                  size = 1.5) +
  # geom_text(data = df.exp1.combined.text,
  #           mapping = aes(x = age_mean,
  #                         y = y,
  #                         label = label),
  #           size = 7,
  #           vjust = -3) +  
  geom_custom(data = df.image,
              mapping = aes(x = x, 
                            y = y, 
                            data = image),
              grob_fun = function(x) x) +
  labs(y = "Percentage of choosing \n the person who prevented \n the worse outcome") +
  coord_cartesian(clip = "off",
                  ylim = c(0, 1)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = str_c(seq(0, 1, 0.25) * 100, "%"),
                     # expand = expansion(add = c(0.05, 0.12))) + 
                     expand = expansion(add = c(0.05, 0))) + 
  scale_x_continuous(breaks = c(seq(3, 7, 1), 8),
                     labels = c(seq(3, 7, 1), "adult"), 
                     expand = expansion(add = c(0.2, 0.5))) +
  scale_fill_gradientn(colors = children_palette) + 
  scale_color_gradientn(colors = children_palette) + 
  theme(axis.text.x = element_text(size = 25),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 25),
        axis.title.y = element_text(size = 25),
        legend.position = "none",
        plot.margin = margin(t = 11,
                             l = 0.5,
                             r = 0.5,
                             b = 0.5,
                             unit = "cm"))

p1
```

### Per trial
```{r fig.width=24, fig.height=10}

set.seed(1)

df.scenarios = tibble(short_name = c("egg_ball",
                                     "icecream_sunscreen",
                                     "vase_bear",
                                     "phone_duck"),
                      long_name = c("egg | basketball", 
                                    "icecream | sunscreen",
                                    "vase | toybear",
                                    "phone | rubberducky"))

# load trial images 
func_load_image = function(scenario){
  readPNG(str_c("../../figures/experiment1/trial_stills/", scenario, ".png"))
}

df.plot = df.exp1_children %>% 
  select(participant, 
         age, 
         age_group, 
         scenario = trial_name, 
         trial_score) %>% 
  bind_rows(df.exp1_adults %>% 
              select(participant,
                     scenario, 
                     trial_score = rating) %>% 
              mutate(age_group = "adults",
                     age = 8) %>% 
              left_join(df.scenarios,
                        by = c("scenario" = "short_name")) %>% 
              select(-scenario) %>% 
              rename(scenario = long_name))

df.plot.means = df.plot %>% 
  group_by(age_group, scenario) %>% 
  summarise(n = n(),
            age_mean = mean(age),
            response = smean.cl.boot(trial_score)) %>%
  mutate(index = c("mean", "low", "high")) %>%
  ungroup() %>% 
  pivot_wider(names_from = index,
              values_from = response)

# plot text showing n for adults + children
df.exp1.combined.text = df.exp1.combinbed.means %>% 
  select(age_group, 
         age_mean, 
         n) %>% 
  mutate(label = n,
         label = ifelse(age_group == "3", 
                        str_c("n = ", n), 
                        n),
         y = 0.95)

# linking images and clips
df.images = df.plot %>% 
  select(scenario) %>% 
  distinct() %>% 
  mutate(grob = map(.x = scenario, 
                    .f = ~ func_load_image(scenario = .x)))

scenario_labels = as_labeller(
  c("egg | basketball" = "basketball | egg",
    "icecream | sunscreen" = "ice cream | sunscreen",
    "vase | toybear" = "bear | vase",
    "phone | rubberducky" = "phone | duck"))

ggplot() + 
  geom_hline(yintercept = seq(0, 1, 0.25),
             linetype = "solid",
             alpha = 0.1) +
  geom_hline(yintercept = 0.5,
             linetype = "dashed") +
  geom_pointrange(data = df.plot.means %>%
                    filter(age_group != "adults"),
                  mapping = aes(x = age_mean,
                                y = mean,
                                ymin = low,
                                ymax = high,
                                fill = age_mean),
                  shape = 21,
                  size = 1.5) +
  geom_pointrange(data = df.plot.means %>%
                    filter(age_group == "adults"),
                  mapping = aes(x = age_mean,
                                y = mean,
                                ymin = low,
                                ymax = high),
                  shape = 23,
                  fill = "grey",
                  size = 1.5) +
  geom_custom(data = df.images,
              mapping = aes(data = grob,
                            x = -Inf,
                            y = Inf),
              grob_fun = function(x) rasterGrob(x,
                                                interpolate = T,
                                                width = 1,
                                                vjust = 0,
                                                hjust = 0)) + 
  facet_wrap(~ scenario,
             nrow = 1,
             labeller = scenario_labels) +
  labs(x = "Age (in years)",
       y = "Percentage of choosing \n worse outcome prevented") +
  coord_cartesian(clip = "off",
                  ylim = c(0, 1)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = str_c(seq(0, 1, 0.25) * 100, "%"),
                     expand = expansion(add = c(0.05, 0.12))) + 
  scale_x_continuous(breaks = c(3, 4, 5, 6, 7, 8),
                     labels = c("3", "4", "5", "6", "7", "adult"),
                     limits = c(3, 8), 
                     expand = expansion(add = c(0, 0.5))) +
  scale_fill_gradientn(colors = children_palette) + 
  scale_color_gradientn(colors = children_palette) + 
  theme(axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title = element_text(size = 25),
        axis.title.x = element_blank(),
        strip.background = element_blank(),
        plot.title = element_blank(),
        panel.spacing.x = unit(2, units = "cm"),
        strip.text = element_text(size = 32,
                                  vjust = 39,
                                  face = "bold"),
        legend.position = "none",
        plot.margin = margin(t = 12,
                             l = 0.5,
                             r = 0.5,
                             b = 0.5,
                             unit = "cm"))

ggsave(filename = "../../figures/experiment1/exp1_results_trials.pdf",
       width = 24,
       height = 10)

```



# EXPERIMENT 2 

## CHILDREN

### DATA

#### Read in Data
```{r}

df.exp2_children = read_csv("../../data/experiment2/children/exp2_children.csv", show_col_types = F) 

```

#### Wrangle
```{r}

df.exp2_children = df.exp2_children %>%
  filter(row_number() >= 0 & row_number() <= 120) %>% 
  select(age, 
         gender, 
         lan_spoken, 
         trial_1, 
         trial_1_score, 
         trial_2, 
         trial_2_score, 
         trial_3, 
         trial_3_score, 
         trial_4, 
         trial_4_score, 
         trial_5, 
         trial_5_score, 
         trial_6, 
         trial_6_score, 
         total_score) %>%
  mutate(age_group = cut(age, breaks = c(3, 4, 5, 6, 7.1),
                         labels = c("3", "4", "5", "6"),
                         right = TRUE)) %>%
  na.omit() %>%
  mutate(participant = 1:n(),
         total_score = as.numeric(total_score),
         across("trial_1"|"trial_2"|"trial_3"|"trial_4"|"trial_5"|"trial_6", ~case_when(
           grepl("lightbulb_laundry_correct_(left|right)_(jessie|caleb)", .) ~ "lightbulb",
           grepl("apple_trashcan_correct_(left|right)_(lily|alex)", .) ~ "apple",
           grepl("basketball_egg_correct_(left|right)_(charlie|noah)", .) ~ "basketball",
           grepl("glass_beanbag_correct_(left|right)_(emily|lucas)", .) ~ "glass",
           grepl("rock_wine_correct_(left|right)_(amber|billy)", .) ~ "rock",
           grepl("bear_water_correct_(left|right)_(vicky|connor)", .) ~ "bear",
           TRUE ~ .
         ))) %>%
  mutate(across(starts_with("trial"), as.character)) %>%
  pivot_longer(cols = c("trial_1", 
                        "trial_2", 
                        "trial_3", 
                        "trial_4", 
                        "trial_5", 
                        "trial_6"),
               names_to = "trial_order",
               values_to = "trial_name") %>%
  group_by(participant) %>%
  mutate(trial_score = case_when(
    trial_order == "trial_1" ~ trial_1_score,
    trial_order == "trial_2" ~ trial_2_score,
    trial_order == "trial_3" ~ trial_3_score,
    trial_order == "trial_4" ~ trial_4_score,
    trial_order == "trial_5" ~ trial_5_score,
    trial_order == "trial_6" ~ trial_6_score,
  )) %>%
  mutate(trial_score = as.numeric(trial_score)) %>%
  mutate(trial_order = str_remove(trial_order, "_")) %>%
  mutate(side = case_when(
    trial_name %in% c("basketball", "bear", "apple", "rock") ~ "side with things",
    trial_name %in% c("lightbulb", "glass") ~ "side with nothing",
    TRUE ~ "Uncategorized" 
  )) %>%
  mutate(prefer_things = case_when(
    side == "side with things" & trial_score == 1 ~ 1,
    side == "side with nothing" & trial_score == 0 ~ 1,
    TRUE ~ 0
  )) %>%
  select(participant, 
         gender, 
         lan_spoken, 
         age, 
         age_group, 
         trial_order, 
         trial_name, 
         trial_score, 
         side, 
         prefer_things, 
         total_score)

```

#### Demographics
```{r}

print_demographics(df.exp2_children)

```

### STATS

#### Hypothesis 1 

Overall, children will thank the individual who prevented the worse outcome from occurring at rates that exceed chance.

```{r}

fit.brm3 = brm(formula = trial_score ~ 1 + (1 | participant) + (1 | trial_name),
               data = df.exp2_children,
               family = "bernoulli", 
               cores = 4,
               file = "cache/brm3") 

fit.brm3 %>% 
  tidy(effects = c("fixed"),
       conf.int = TRUE,
       conf.level = 0.95,
       conf.method = "HPDinterval") %>% 
  mutate(across(.cols = c(estimate, conf.low, conf.high),
                .fns = ~ inv.logit(.))) %>% 
  select(estimate, contains("conf"))

```

#### Hypothesis 2
```{r}

set.seed(1)

# The tendency to thank the individual who prevented the worse potential outcome 
# from occurring will increase with age

fit.brm4 = brm(formula = trial_score ~ 1 + age + (1 | participant) + (1 | trial_name),
               data = df.exp2_children,
               family = "bernoulli", 
               cores = 4,
               file = "cache/brm4") 

fit.brm4 %>% 
  tidy(effects = c("fixed"),
       conf.int = TRUE,
       conf.level = 0.95,
       conf.method = "HPDinterval") %>% 
  filter(term == "age") %>%
  select(estimate, contains("conf")) 

```

##### Above chance performance 
```{r}

# At what age will children perform above chance?

df.exp2_age_grid = tibble(age = seq(min(df.exp2_children$age),
                                    max(df.exp2_children$age),
                                    length.out = 200))

# Get posterior draws of predicted probabilities
preds = posterior_epred(fit.brm4,
                        newdata = df.exp2_age_grid,
                        re_formula = NA)

df.exp2.age.min = as_tibble(t(preds)) %>%
  mutate(age = df.exp2_age_grid$age) %>%
  pivot_longer(-age, 
               names_to = "draw", 
               values_to = "p") %>%
  group_by(age) %>%
  summarise(mean = mean(p),
            lower = quantile(p, 0.025),
            upper = quantile(p, 0.975),
            .groups = "drop")

cross_age = df.exp2.age.min %>%
  filter(lower > 0.5) %>%
  summarise(min_age = min(age)) %>%
  pull(min_age)

fun_plot_above_chance(data = df.exp2.age.min,
                    cross_age = cross_age)

```

## ADULTS

### DATA

#### Read in Data
```{r}

df.exp2_adults = read_csv("../../data/experiment2/adults/exp2_adults.csv", show_col_types = F)

```

#### Wrangle
```{r}

df.exp2_adults = df.exp2_adults %>% 
  mutate(participant = 1:n()) %>% 
  relocate(participant) %>% 
  select(-workerid, -error) %>% 
  pivot_longer(cols = c("video_1", 
                        "video_2", 
                        "video_3", 
                        "video_4", 
                        "video_5", 
                        "video_6"),
               names_to = "video_version",
               values_to = "video") %>% 
  pivot_longer(cols = c("video_1_correct_answer", 
                        "video_2_correct_answer", 
                        "video_3_correct_answer", 
                        "video_4_correct_answer", 
                        "video_5_correct_answer", 
                        "video_6_correct_answer"),
               names_to = "video_version_correct_answer",
               values_to = "correct_answer") %>% 
  pivot_longer(cols = c("video_1_response", 
                        "video_2_response", 
                        "video_3_response", 
                        "video_4_response", 
                        "video_5_response", 
                        "video_6_response"),
               names_to = "video_version_response",
               values_to = "response") %>% 
  mutate(video_version_correct_answer = str_remove_all(video_version_correct_answer, "_correct_answer"),
         video_version_response = str_remove_all(video_version_response, "_response")) %>% 
  filter(video_version == video_version_correct_answer & video_version_correct_answer == video_version_response) %>% 
  mutate(age = "Adult") %>%
  select(age, 
         participant, 
         scenario = video, 
         correct_answer, 
         response) %>% 
  mutate(rating = if_else(correct_answer == response, 1, 0)) %>%
  rename(trial_response = response,
         response = rating) 

```

#### Demographics
```{r}

df.exp2_adults_demographics = read_csv("../../data/experiment2/adults/exp2_adults_demographics.csv", show_col_types = F) 

print_demographics_adults(df.exp2_adults_demographics)

```

### STATS

#### Hypothesis 1 

Overall, adults will thank the individual who prevented the worse outcome from occurring at rates that exceed chance.

```{r}

fit.brm3.adults = brm(formula = response ~ 1 + (1 | participant) + (1 | scenario),
                      data = df.exp2_adults ,
                      family = "bernoulli",
                      cores = 4,
                      file = "cache/brm3.adults") 

fit.brm3.adults %>% 
  tidy(effects = c("fixed"),
       conf.int = TRUE,
       conf.level = 0.95,
       conf.method = "HPDinterval") %>% 
  mutate(across(.cols = c(estimate, conf.low, conf.high),
                .fns = ~ inv.logit(.))) %>% 
  select(estimate, contains("conf")) 

```

## PLOTS

### Overall 

```{r fig.height=12, fig.width=6}

set.seed(1)

# Load image as grob
overall_image = readPNG("../../figures/experiment2/overall_still/experiment2.png")
overall_grob = rasterGrob(overall_image, 
                          interpolate = TRUE, 
                          width = 1, 
                          vjust = -0.1, 
                          hjust = 0)

# Create a dataframe with the grob in a column named `image`
df.image = tibble(x = -Inf,
                  y = Inf,
                  image = list(overall_grob),
                  facet_var = "Experiment 2")

# INDIVIDUAL DATA 

# children
df.exp2.children.individual = df.exp2_children %>%
  select(participant, 
         age_group, 
         age, 
         total_score) %>% 
  distinct() %>% 
  mutate(pct_correct = total_score / 6) %>% 
  select(-total_score) %>% 
  mutate(facet_var = "Experiment 2")

# adults
df.exp2.adults.individual = df.exp2_adults %>%
  rename(trial_name = scenario) %>%
  group_by(participant) %>%
  summarise(total_score = sum(response),
            pct_correct = total_score / 6) %>%
  ungroup() %>%
  mutate(age_group = "adults",
         age = 8) %>% 
  select(-total_score)

# combine total counterfactual data for adults + children
df.combined.individual = bind_rows(df.exp2.children.individual,
                                   df.exp2.adults.individual)

# MEANS 
df.exp2.combinbed.means = df.combined.individual %>% 
  group_by(age_group) %>% 
  summarise(
    n = n(),
    age_mean = mean(age),
    response = smean.cl.boot(pct_correct)) %>%
  mutate(index = c("mean", "low", "high")) %>%
  ungroup() %>% 
  pivot_wider(names_from = index,
              values_from = response)

# plot text showing n for adults + children
# df.exp2.combined.text = df.exp2.combinbed.means %>% 
#   select(age_group, age_mean, n) %>% 
#   mutate(label = n,
#          y = 0.95)

p2 = ggplot() + 
  geom_hline(yintercept = seq(0, 1, 0.25),
             linetype = "solid",
             alpha = 0.1) +
  geom_hline(yintercept = 0.5,
             linetype = "dashed") +
  geom_ribbon(data = df.exp2.age.min,
              aes(x = age, 
                  ymin = lower, 
                  ymax = upper),
              inherit.aes = FALSE,
              alpha = 0.2, 
              fill = "darkgreen") +
  geom_line(data = df.exp2.age.min,
            aes(x = age, 
                y = mean),
            inherit.aes = FALSE,
            color = "darkgreen", 
            size = 1) +
  geom_point(data = df.exp2.children.individual,
             mapping = aes(x = age,
                           y = pct_correct,
                           fill = age,
                           color = age),
             shape = 21,
             size = 2,
             color = "grey30",
             alpha = .4) +
  geom_pointrange(data = df.exp2.combinbed.means %>%
                    filter(age_group != "adults"),
                  mapping = aes(x = age_mean,
                                y = mean,
                                ymin = low,
                                ymax = high,
                                fill = age_mean),
                  shape = 21,
                  size = 1.5) +
  geom_pointrange(data = df.exp2.combinbed.means %>%
                    filter(age_group == "adults"),
                  mapping = aes(x = age_mean,
                                y = mean,
                                ymin = low,
                                ymax = high),
                  shape = 23,
                  fill = "grey",
                  size = 1.5) +
  # geom_text(data = df.exp2.combined.text,
  #           mapping = aes(x = age_mean,
  #                         y = y,
  #                         label = label),
  #           size = 7,
  #           vjust = -3) +  
  geom_custom(data = df.image,
              mapping = aes(x = x, 
                            y = y, 
                            data = image),
              grob_fun = function(x) x) +
  coord_cartesian(clip = "off",
                  ylim = c(0, 1)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = str_c(seq(0, 1, 0.25) * 100, "%"),
                     expand = expansion(add = c(0.05, 0))) + 
  scale_x_continuous(breaks = c(seq(3, 7, 1), 8),
                     labels = c(seq(3, 7, 1), "adult"), 
                     expand = expansion(add = c(0.2, 0.5))) +
  scale_fill_gradientn(colors = children_palette) + 
  scale_color_gradientn(colors = children_palette) + 
  theme(axis.text.x = element_text(size = 25),
        axis.title.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "none",
        plot.margin = margin(t = 15,
                             l = 0.5,
                             r = 0.5,
                             b = 0.5,
                             unit = "cm"))

p2
```


### Per trial
```{r fig.width=33, fig.height=10}

set.seed(1)

df.scenarios = tibble(short_name = c("bear",
                                     "lightbulb",
                                     "glass",
                                     "basketball",
                                     "apple",
                                     "rock"))

# load trial images 
func_load_image = function(scenario){
  readPNG(str_c("../../figures/experiment2/trial_stills/", scenario, ".png"))
}

df.plot = df.exp2_children %>% 
  select(participant, 
         age,
         age_group, 
         scenario = trial_name, 
         trial_score) %>% 
  bind_rows(df.exp2_adults %>% 
              select(participant, 
                     scenario, 
                     trial_score = response) %>% 
              mutate(age_group = "adults",
                     age = 8) %>% 
              left_join(df.scenarios,
                        by = c("scenario" = "short_name"))) %>% 
  ungroup()

df.plot.means = df.plot %>% 
  group_by(age_group, scenario) %>% 
  summarise(
    n = n(),
    age_mean = mean(age),
    response = smean.cl.boot(trial_score)) %>%
  mutate(index = c("mean", "low", "high")) %>%
  ungroup() %>% 
  pivot_wider(names_from = index,
              values_from = response)

# plot text showing n for adults + children
df.exp2.combined.text = df.exp2.combinbed.means %>% 
  select(age_group, age_mean, n) %>% 
  mutate(label = n,
         label = ifelse(age_group == "3", str_c("n = ", n), n),
         y = 0.95)

df.images = df.plot %>% 
  select(scenario) %>% 
  distinct() %>% 
  mutate(grob = map(.x = scenario, 
                    .f = ~ func_load_image(.x)))

scenario_labels = as_labeller(
  c("bear" = "bears & dirty water",
    "lightbulb" = "lightbulbs & laundry",
    "glass" = "glasses & pillow",
    "basketball" = "basketballs & eggs",
    "apple" = "apples & trash",
    "rock" = "rocks & glasses"))

ggplot() + 
  geom_hline(yintercept = seq(0, 1, 0.25),
             linetype = "solid",
             alpha = 0.1) +
  geom_hline(yintercept = 0.5,
             linetype = "dashed") +
  geom_pointrange(data = df.plot.means %>%
                    filter(age_group != "adults"),
                  mapping = aes(x = age_mean,
                                y = mean,
                                ymin = low,
                                ymax = high,
                                fill = age_mean),
                  shape = 21,
                  size = 1.5) +
  geom_pointrange(data = df.plot.means %>%
                    filter(age_group == "adults"),
                  mapping = aes(x = age_mean,
                                y = mean,
                                ymin = low,
                                ymax = high),
                  shape = 23,
                  fill = "grey",
                  size = 1.5) +
  geom_custom(data = df.images,
              mapping = aes(data = grob, 
                            x = -Inf, 
                            y = Inf),
              grob_fun = function(x) rasterGrob(x, 
                                                interpolate = TRUE, 
                                                width = 1, 
                                                vjust = 0, 
                                                hjust = 0)) +
  facet_wrap(~ scenario,
             nrow = 1,
             labeller = scenario_labels) +
  labs(x = "Age (in years)",
       y = "Percentage of choosing \n worse outcome prevented") +
  coord_cartesian(clip = "off",
                  ylim = c(0, 1)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = str_c(seq(0, 1, 0.25) * 100, "%"),
                     expand = expansion(add = c(0.05, 0.12))) + 
  scale_x_continuous(
    breaks = c(3, 4, 5, 6, 7, 8),
    labels = c("3", "4", "5", "6", "7", "adult"),
    limits = c(3, 8), 
    expand = expansion(add = c(0, 0.5))  
  ) +
  scale_fill_gradientn(colors = children_palette) + 
  scale_color_gradientn(colors = children_palette) + 
  theme(axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title = element_text(size = 25),
        axis.title.x = element_blank(),
        strip.background = element_blank(),
        plot.title = element_blank(),
        panel.spacing.x = unit(2, units = "cm"),
        strip.text = element_text(size = 34,
                                  vjust = 35,
                                  face = "bold"),
        legend.position = "none",
        plot.margin = margin(t = 12,
                             l = 0.5,
                             r = 0.5,
                             b = 0.5,
                             unit = "cm"))

ggsave(filename = "../../figures/experiment2/exp2_results_trials.pdf",
       width = 34,
       height = 10)

```


# EXPERIMENT 3

## CHILDREN

### DATA

#### Read in Data
```{r}

df.exp3_children = read_csv("../../data/experiment3/children/exp3_children.csv", show_col_types = F)

```

#### Wrangle
```{r}

df.exp3_children = df.exp3_children %>%
  filter(row_number() >= 0 & row_number() <= 240) %>% 
  select(age, 
         gender, 
         lan_spoken, 
         trial_1, 
         trial_1_score, 
         trial_2, 
         trial_2_score, 
         trial_3, 
         trial_3_score, 
         trial_4, 
         trial_4_score, 
         trial_5, 
         trial_5_score, 
         trial_6, 
         trial_6_score, 
         total_score) %>%
  mutate(age_group = cut(age, breaks = c(3, 4, 5, 6, 7, 8, 9, 10, 11.1),
                         labels = c("3", "4", "5", "6", "7", "8", "9", "10"),
                         right = TRUE)) %>%
  na.omit() %>%
  mutate(participant = 1:n(),
         total_score = as.numeric(total_score),
         across("trial_1"|"trial_2"|"trial_3"|"trial_4"|"trial_5"|"trial_6", ~case_when(
           grepl("exp7_bulb_laundry_correct_(left|right)_(jessie|caleb)", .) ~ "lightbulb",
           grepl("exp7_apple_trashcan_correct_(left|right)_(lily|alex)", .) ~ "apple",
           grepl("exp7_basketball_egg_correct_(left|right)_(charlie|noah)", .) ~ "basketball",
           grepl("exp7_glass_beanbag_correct_(left|right)_(emily|lucas)", .) ~ "glass",
           grepl("exp7_rock_wine_correct_(left|right)_(amber|billy)", .) ~ "rock",
           grepl("exp7_bear_water_correct_(left|right)_(vicky|connor)", .) ~ "bear",
           TRUE ~ .
         ))) %>%
  mutate(across(starts_with("trial"), as.character)) %>%
  pivot_longer(cols = c("trial_1", 
                        "trial_2", 
                        "trial_3", 
                        "trial_4", 
                        "trial_5", 
                        "trial_6"),
               names_to = "trial_order",
               values_to = "trial_name") %>%
  group_by(participant) %>%
  mutate(trial_score = case_when(
    trial_order == "trial_1" ~ trial_1_score,
    trial_order == "trial_2" ~ trial_2_score,
    trial_order == "trial_3" ~ trial_3_score,
    trial_order == "trial_4" ~ trial_4_score,
    trial_order == "trial_5" ~ trial_5_score,
    trial_order == "trial_6" ~ trial_6_score)) %>%
  mutate(trial_score = as.numeric(trial_score)) %>%
  mutate(trial_order = str_remove(trial_order, "_")) %>%
  mutate(side = case_when(
    trial_name %in% c("basketball", "bear", "apple", "rock") ~ "side with things",
    trial_name %in% c("lightbulb", "glass") ~ "side with nothing",
    TRUE ~ "Uncategorized" 
  )) %>%
  mutate(prefer_things = case_when(
    side == "side with things" & trial_score == 1 ~ 1,
    side == "side with nothing" & trial_score == 0 ~ 1,
    TRUE ~ 0
  )) %>%
  select(participant, 
         gender, 
         lan_spoken, 
         age, 
         age_group, 
         trial_order, 
         trial_name, 
         trial_score, 
         side, 
         prefer_things, 
         total_score)

```


#### Demographics
```{r}

print_demographics(df.exp3_children)

```

### STATS

#### Hypothesis 1 

Overall, children will thank the individual who prevented the worse outcome from occurring at rates that exceed chance. 

```{r}

fit.brm5.children = brm(formula = trial_score ~ 1 + (1 | participant) + (1 | trial_name),
                        data = df.exp3_children,
                        family = "bernoulli", 
                        cores = 4,
                        file = "cache/brm5") 

fit.brm5.children %>% 
  tidy(effects = c("fixed"),
       conf.int = TRUE,
       conf.level = 0.95,
       conf.method = "HPDinterval") %>% 
  mutate(across(.cols = c(estimate, conf.low, conf.high),
                .fns = ~ inv.logit(.))) %>% 
  select(estimate, contains("conf"))

```

#### Hypothesis 2

The tendency to thank the individual who prevented the worse potential outcome from occurring will increase with age.

```{r}

fit.brm5.children.age = brm(formula = trial_score ~ 1 + age + (1 | participant) + (1 | trial_name),
                            data = df.exp3_children,
                            family = "bernoulli", 
                            cores = 4,
                            file = "cache/brm6") 

fit.brm5.children.age %>% 
  tidy(effects = c("fixed"),
       conf.int = TRUE,
       conf.level = 0.95,
       conf.method = "HPDinterval") %>% 
  filter(term == "age") %>%
  select(estimate, contains("conf")) 

```

#### Above chance performance (all children)

At what age will children perform above chance?

```{r}

df.exp3_age_grid = tibble(age = seq(min(df.exp3_children$age),
                                    max(df.exp3_children$age),
                                    length.out = 200))

# Posterior predictions
preds = posterior_epred(fit.brm5.children.age, 
                        newdata = df.exp3_age_grid, 
                        re_formula = NA)

df.exp3.age.min = as_tibble(t(preds)) %>%
  mutate(age = df.exp3_age_grid$age) %>%
  pivot_longer(-age, 
               names_to = "draw", 
               values_to = "p") %>%
  group_by(age) %>%
  summarise(mean = mean(p),
            lower = quantile(p, 0.025),
            upper = quantile(p, 0.975),
            .groups = "drop")

cross_age = df.exp3.age.min %>%
  filter(lower > 0.5) %>%
  summarise(min_age = min(age)) %>%
  pull(min_age)

fun_plot_above_chance(data = df.exp3.age.min,
                    cross_age = cross_age)

```

#### Above chance performance (younger children only)

At what age will children perform above chance?

```{r}

df.exp3_children_younger = df.exp3_children %>%
  filter(age <= 7)

fit.brm7.children.age = brm(formula = trial_score ~ 1 + age + (1 | participant) + (1 | trial_name),
                            data = df.exp3_children_younger,
                            family = "bernoulli", 
                            cores = 4,
                            file = "cache/brm7") 


# At what age will children younger than 7 perform above chance?

df.exp3_age_grid = tibble(age = seq(min(df.exp3_children_younger$age),
                                    max(df.exp3_children_younger$age),
                                    length.out = 200))

# Posterior predictions
preds = posterior_epred(fit.brm7.children.age, 
                        newdata = df.exp3_age_grid, 
                        re_formula = NA)

df.exp3.age.min.restricted = as_tibble(t(preds)) %>%
  mutate(age = df.exp3_age_grid$age) %>%
  pivot_longer(-age, 
               names_to = "draw", 
               values_to = "p") %>%
  group_by(age) %>%
  summarise(mean = mean(p),
            lower = quantile(p, 0.025),
            upper = quantile(p, 0.975),
            .groups = "drop")

cross_age = df.exp3.age.min %>%
  filter(lower > 0.5) %>%
  summarise(min_age = min(age)) %>%
  pull(min_age)

fun_plot_above_chance(data = df.exp3.age.min.restricted,
                      cross_age = cross_age)

```

## ADULTS

### DATA

#### Read in Data
```{r}

file_names = list.files(path = "../../data/experiment3/adults/",
                        pattern = "*.csv")

df.exp3_adults = map_dfr(.x = file_names,
                         .f = ~ read_csv(str_c("../../data/experiment3/adults/", .x),
                                         show_col_types = F),
                         .id = "participant")

```

#### Demographics
```{r}

print_demographics_adults(df.exp3_adults)

```

#### Wrangle
```{r}

df.exp3_adults = df.exp3_adults %>%
  mutate(participant = as.numeric(participant)) %>% 
  pivot_longer(cols = c("video_1", 
                        "video_2", 
                        "video_3", 
                        "video_4", 
                        "video_5", 
                        "video_6"),
  names_to = "video_version",
  values_to = "video") %>% 
  pivot_longer(cols = c("video_1_correct_answer", 
                        "video_2_correct_answer", 
                        "video_3_correct_answer", 
                        "video_4_correct_answer", 
                        "video_5_correct_answer", 
                        "video_6_correct_answer"),
               names_to = "video_version_correct_answer",
               values_to = "correct_answer") %>% 
  pivot_longer(cols = c("video_1_response", 
                        "video_2_response", 
                        "video_3_response", 
                        "video_4_response", 
                        "video_5_response", 
                        "video_6_response"),
               names_to = "video_version_response",
               values_to = "response") %>% 
  mutate(video_version_correct_answer = str_remove_all(video_version_correct_answer, "_correct_answer"),
         video_version_response = str_remove_all(video_version_response, "_response")) %>% 
  filter(video_version == video_version_correct_answer & video_version_correct_answer == video_version_response) %>% 
  mutate(age = "Adult") %>%
  select(age, 
         participant, 
         scenario = video, 
         correct_answer, 
         response, 
         feedback) %>% 
  mutate(rating = if_else(correct_answer == response, 1, 0)) %>%
  rename(trial_response = response,
         response = rating) 

```

### STATS

#### Hypothesis 1 

Overall adults will thank the individual who prevented the worse outcome from occurring at rates that exceed chance. 

```{r}

fit.brm5.adults = brm(formula = response ~ 1 + (1 | participant) + (1 | scenario),
                      data = df.exp3_adults,
                      family = "bernoulli",
                      cores = 4,
                      file = "cache/brm5_adults") 

fit.brm5.adults %>% 
  tidy(effects = c("fixed"),
       conf.int = TRUE,
       conf.level = 0.95,
       conf.method = "HPDinterval") %>% 
  mutate(across(.cols = c(estimate, conf.low, conf.high),
                .fns = ~ inv.logit(.))) %>% 
  select(estimate, contains("conf")) 

```

## PLOTS

### Overall

```{r fig.height=12, fig.width=9}

set.seed(1)

# Load image as grob
overall_image = readPNG("../../figures/experiment3/overall_still/experiment3.png")
overall_grob = rasterGrob(overall_image, 
                          interpolate = TRUE, 
                          width = 1, 
                          vjust = -0.1, 
                          hjust = 0)

# Create a dataframe with the grob in a column named `image`
df.image = tibble(x = -Inf,
                  y = Inf,
                  image = list(overall_grob))

# INDIVIDUAL DATA 

# children
df.exp3.children.individual = df.exp3_children %>%
  select(participant, 
         age_group, 
         age, 
         total_score) %>% 
  distinct() %>% 
  mutate(pct_correct = total_score / 6) %>% 
  select(-total_score)

# adults
df.exp3.adults.individual = df.exp3_adults %>%
  rename(trial_name = scenario) %>%
  group_by(participant) %>%
  summarise(total_score = sum(response),
            pct_correct = total_score / 6) %>%
  ungroup() %>%
  mutate(age_group = "adults",
         age = 12) %>% 
  select(-total_score)

# combine total counterfactual data for adults + children
df.combined.individual = bind_rows(df.exp3.children.individual,
                                   df.exp3.adults.individual)

# MEANS 
df.exp3.combined.means = df.combined.individual %>% 
  group_by(age_group) %>% 
  summarise(
    n = n(),
    age_mean = mean(age),
    response = smean.cl.boot(pct_correct)) %>%
  mutate(index = c("mean", "low", "high")) %>%
  ungroup() %>% 
  pivot_wider(names_from = index,
              values_from = response)

# plot text showing n for adults + children
# df.exp3.combined.text = df.exp3.combinbed.means %>% 
#   select(age_group, age_mean, n) %>% 
#   mutate(label = n,
#          y = 0.95)

p3 = ggplot() + 
  geom_hline(yintercept = seq(0, 1, 0.25),
             linetype = "solid",
             alpha = 0.1) +
  geom_hline(yintercept = 0.5,
             linetype = "dashed") +
  geom_ribbon(data = df.exp3.age.min,
              aes(x = age, 
                  ymin = lower, 
                  ymax = upper),
              inherit.aes = FALSE,
              alpha = 0.2, 
              fill = "darkgreen") +
  geom_line(data = df.exp3.age.min,
            aes(x = age, 
                y = mean),
            inherit.aes = FALSE,
            color = "darkgreen", 
            size = 1) +
  geom_point(data = df.exp3.children.individual,
             mapping = aes(x = age,
                           y = pct_correct,
                           fill = age,
                           color = age),
             shape = 21,
             size = 2,
             color = "grey30",
             alpha = .4) +
  geom_pointrange(data = df.exp3.combined.means %>%
                    filter(age_group != "adults"),
                  mapping = aes(x = age_mean,
                                y = mean,
                                ymin = low,
                                ymax = high,
                                fill = age_mean),
                  shape = 21,
                  size = 1.5) +
  geom_pointrange(data = df.exp3.combinbed.means %>%
                    filter(age_group == "adults"),
                  mapping = aes(x = age_mean,
                                y = mean,
                                ymin = low,
                                ymax = high),
                  shape = 23,
                  fill = "grey",
                  size = 1.5) +
  # geom_text(data = df.exp3.combined.text,
  #           mapping = aes(x = age_mean,
  #                         y = y,
  #                         label = label),
  #           size = 7,
  #           vjust = -3) +  
  geom_custom(data = df.image,
              mapping = aes(x = x, 
                            y = y, 
                            data = image),
              grob_fun = function(x) x) +
  coord_cartesian(clip = "off",
                  ylim = c(0, 1)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = str_c(seq(0, 1, 0.25) * 100, "%"),
                     expand = expansion(add = c(0.05, 0))) + 
  scale_x_continuous(breaks = c(seq(3, 11, 1), 12),
                     labels = c(seq(3, 11, 1), "adult"), 
                     expand = expansion(add = c(0.2, 0.5))) +
  scale_fill_gradientn(colors = children_palette) + 
  scale_color_gradientn(colors = children_palette) + 
  theme(axis.text.x = element_text(size = 25),
        axis.title.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y = element_blank(),,
        legend.position = "none",
        plot.margin = margin(t = 22,
                             l = 0.5,
                             r = 0.5,
                             b = 0.5,
                             unit = "cm"))

p3
```

### Per trial
```{r fig.width=44, fig.height=10}

set.seed(1)

df.scenarios = tibble(short_name = c("bear",
                                     "lightbulb",
                                     "glass",
                                     "basketball",
                                     "apple",
                                     "rock"))

# load trial images 
func_load_image = function(scenario){
  readPNG(str_c("../../figures/experiment3/trial_stills/", scenario, ".png"))
}

df.plot = df.exp3_children %>% 
  select(participant, 
         age, 
         age_group, 
         scenario = trial_name, 
         trial_score) %>% 
  bind_rows(df.exp3_adults %>% 
              select(participant, 
                     scenario, 
                     trial_score = response) %>% 
              mutate(age_group = "adults",
                     age = 12) %>% 
              left_join(df.scenarios,
                        by = c("scenario" = "short_name"))) %>% 
  ungroup()

df.plot.means = df.plot %>% 
  group_by(age_group, scenario) %>% 
  summarise(n = n(),
            age_mean = mean(age),
            response = smean.cl.boot(trial_score)) %>%
  mutate(index = c("mean", "low", "high")) %>%
  ungroup() %>% 
  pivot_wider(names_from = index,
              values_from = response)

# plot text showing n for adults + children
df.exp3.combined.text = df.exp3.combinbed.means %>% 
  select(age_group, 
         age_mean, 
         n) %>% 
  mutate(label = n,
         label = ifelse(age_group == "3", 
                        str_c("n = ", n), 
                        n),
         y = 0.95)

df.images = df.plot %>% 
  select(scenario) %>% 
  distinct() %>% 
  mutate(grob = map(.x = scenario, 
                    .f = ~ func_load_image(.x)))

scenario_labels = as_labeller(
  c("bear" = "bears & dirty water",
    "lightbulb" = "lightbulbs & laundry",
    "glass" = "glasses & pillow",
    "basketball" = "basketballs & eggs",
    "apple" = "apples & trash",
    "rock" = "rocks & glasses"))

ggplot() + 
  geom_hline(yintercept = seq(0, 1, 0.25),
             linetype = "solid",
             alpha = 0.1) +
  geom_hline(yintercept = 0.5,
             linetype = "dashed") +
  geom_pointrange(data = df.plot.means %>%
                    filter(age_group != "adults"),
                  mapping = aes(x = age_mean,
                                y = mean,
                                ymin = low,
                                ymax = high,
                                fill = age_mean),
                  shape = 21,
                  size = 1.5) +
  geom_pointrange(data = df.plot.means %>%
                    filter(age_group == "adults"),
                  mapping = aes(x = age_mean,
                                y = mean,
                                ymin = low,
                                ymax = high),
                  shape = 23,
                  fill = "grey",
                  size = 1.5) +
  geom_custom(data = df.images,
              mapping = aes(data = grob, 
                            x = -Inf, 
                            y = Inf),
              grob_fun = function(x) rasterGrob(x, 
                                                interpolate = TRUE, 
                                                width = 1, 
                                                vjust = 0, 
                                                hjust = 0)) +
  facet_wrap(~ scenario,
             nrow = 1,
             labeller = scenario_labels) +
  labs(x = "Age (in years)",
       y = "Percentage of choosing \n worse outcome prevented") +
  coord_cartesian(clip = "off",
                  ylim = c(0, 1)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = str_c(seq(0, 1, 0.25) * 100, "%"),
                     expand = expansion(add = c(0.05, 0.12))) + 
  scale_x_continuous(
    breaks = c(3, 4, 5, 6, 7, 8, 9, 10, 11, 12),
    labels = c("3", "4", "5", "6", "7", "8", "9", "10", "11", "adult"),
    limits = c(3, 12), 
    expand = expansion(add = c(0, 0.5))  
  ) +
  scale_fill_gradientn(colors = children_palette) + 
  scale_color_gradientn(colors = children_palette) + 
  theme(axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title = element_text(size = 25),
        axis.title.x = element_blank(),
        strip.background = element_blank(),
        plot.title = element_blank(),
        panel.spacing.x = unit(2, units = "cm"),
        strip.text = element_text(size = 45,
                                  vjust = 36,
                                  face = "bold"),
        legend.position = "none",
        plot.margin = margin(t = 12.2,
                             l = 0.5,
                             r = 0.5,
                             b = 0.5,
                             unit = "cm"))

ggsave(filename = "../../figures/experiment3/exp3_results_trials.pdf",
       width = 44,
       height = 10)

```

# COMBINED

## PLOTS 
```{r fig.height=12, fig.width=20}

# Combine the plots horizontally

p1x = p1 + labs(title = "A          Experiment 1")
p2x = p2 + labs(title = "B          Experiment 2")
p3x = p3 + labs(title = "C          Experiment 3")

p1x + p2x + p3x +
  plot_layout(ncol = 3) &
  theme(plot.title = element_text(size = 30,
                                  face = "bold",
                                  vjust = 52,
                                  hjust = 0),
        plot.margin = margin(t = 7,
                             l = 0.5,
                             r = 0.5,
                             b = 0.5,
                             unit = "cm"))

ggsave(filename = "../../figures/overall_results.pdf",
       width = 20,
       height = 12)
```
# APPENDIX

# EXPERIMENT 1 (What children like and what Granny likes)

# DATA

## Read in Data
```{r message=FALSE, warning=FALSE}

df.exp1_appendix = read_csv("../../data/experiment1_appendix/exp1_appendix_children.csv")

```

## Wrangle
```{r message=FALSE, warning=FALSE}

df.exp1_appendix = df.exp1_appendix %>% 
  filter(row_number() >= 0 & row_number() <= 120) %>% 
  select(order, 
         age, 
         gender, 
         lan_spoken, 
         trial_1, 
         trial_1_score, 
         trial_2, 
         trial_2_score, 
         trial_3, 
         trial_3_score, 
         trial_4, 
         trial_4_score, 
         trial_1_to_4_total_score, 
         trial_5, 
         trial_5_score, 
         trial_6, 
         trial_6_score, 
         trial_7, 
         trial_7_score, 
         trial_8, 
         trial_8_score, 
         trial_5_to_8_total_score) %>%
  mutate(age_group = cut(age, breaks = c(3, 4, 5, 6, 7.1),
                         labels = c("3", "4", "5", "6"),
                         right = TRUE)) %>%
  mutate(participant = 1:n(),
         child_total = as.numeric(trial_1_to_4_total_score),
         granny_total = as.numeric(trial_5_to_8_total_score),
         across("trial_1"|"trial_2"|"trial_3"|"trial_4"|"trial_5"|"trial_6"|"trial_7"|"trial_8", ~case_when(
           grepl("(order1|order2)_(egg|basketball)_(left|right)_(egg|basketball)_(left|right)_granny", .) ~ "egg | basketball",
           grepl("(order1|order2)_(phone|duck)_(left|right)_(phone|duck)_(left|right)_granny", .) ~ "phone | ducky",
           grepl("(order1|order2)_(vase|bear)_(left|right)_(vase|bear)_(left|right)_granny", .) ~ "vase | bear",
           grepl("(order1|order2)_(icecream|sunscreen)_(left|right)_(icecream|sunscreen)_(left|right)_granny", .) ~ "icecream | sunscreen",
           grepl("(order1|order2)_(egg|basketball)_(left|right)_(egg|basketball)_(left|right)", .) ~ "egg | basketball",
           grepl("(order1|order2)_(phone|duck)_(left|right)_(phone|duck)_(left|right)", .) ~ "phone | ducky",
           grepl("(order1|order2)_(vase|bear)_(left|right)_(vase|bear)_(left|right)", .) ~ "vase | bear",
           grepl("(order1|order2)_(icecream|sunscreen)_(left|right)_(icecream|sunscreen)_(left|right)", .) ~ "icecream | sunscreen",
           TRUE ~ .
         ))) %>%
  mutate(across(starts_with("trial"), 
                as.character)) %>%
  pivot_longer(cols = c("trial_1", 
                        "trial_2", 
                        "trial_3", 
                        "trial_4", 
                        "trial_5", 
                        "trial_6", 
                        "trial_7", 
                        "trial_8"),
               names_to = "trial_order",
               values_to = "trial_name") %>%
  group_by(participant) %>%
  mutate(trial_score = case_when(
    trial_order == "trial_1" ~ trial_1_score,
    trial_order == "trial_2" ~ trial_2_score,
    trial_order == "trial_3" ~ trial_3_score,
    trial_order == "trial_4" ~ trial_4_score,
    trial_order == "trial_5" ~ trial_5_score,
    trial_order == "trial_6" ~ trial_6_score,
    trial_order == "trial_7" ~ trial_7_score,
    trial_order == "trial_8" ~ trial_8_score,
  )) %>%
  mutate(trial_score = as.numeric(trial_score)) %>%
  mutate(trial_order = paste("trial", str_extract(trial_order, "\\d+"), 
                             sep = " ")) %>%
  mutate(section = case_when(
    (order == 1 & trial_order %in% c("trial 1", 
                                     "trial 2", 
                                     "trial 3", 
                                     "trial 4")) ~ "child_preference",
    (order == 1 & trial_order %in% c("trial 5", 
                                     "trial 6", 
                                     "trial 7", 
                                     "trial 8")) ~ "granny_preference",
    (order == 2 & trial_order %in% c("trial 1", 
                                     "trial 2", 
                                     "trial 3", 
                                     "trial 4")) ~ "granny_preference",
    (order == 2 & trial_order %in% c("trial 5", 
                                     "trial 6", 
                                     "trial 7", 
                                     "trial 8")) ~ "child_preference",
    TRUE ~ NA_character_
  )) %>% 
  mutate(trial_order_sectional = case_when(
    trial_order == "trial 1" ~ "trial 1",
    trial_order == "trial 2" ~ "trial 2",
    trial_order == "trial 3" ~ "trial 3",
    trial_order == "trial 4" ~ "trial 4",
    trial_order == "trial 5" ~ "trial 1",
    trial_order == "trial 6" ~ "trial 2",
    trial_order == "trial 7" ~ "trial 3",
    trial_order == "trial 8" ~ "trial 4",
    TRUE ~ trial_order 
  )) %>%
  select(order, 
         participant, 
         gender, 
         lan_spoken, 
         age, 
         age_group, 
         trial_order, 
         trial_order_sectional, 
         trial_name, 
         trial_score, 
         section, 
         child_total, 
         granny_total)

```
  
  

## Demographics
```{r}

print_demographics(df.exp1_appendix)

```

# PLOTS

## Overall

```{r}

set.seed(1)

df.exp1_children_original = df.exp1_children %>%
  mutate(trial_order_sectional = trial_order,
         order = 0,
         section = "counterfactual") %>%
  select(order, 
         participant, 
         gender, 
         lan_spoken, 
         age, 
         age_group, 
         trial_order, 
         trial_order_sectional, 
         trial_name, 
         trial_score, 
         section, 
         total_score) %>%
  rename(test_total = total_score) 


df.combined = bind_rows(df.exp1_children_original, df.exp1_appendix) %>%
  mutate(section_total = case_when(
    section == "counterfactual" ~ test_total,
    section == "child_preference" ~ child_total,
    section == "granny_preference" ~ granny_total,
    TRUE ~ NA_real_),
    section = factor(section, levels = c("counterfactual",
                                         "child_preference",
                                         "granny_preference")),
    age_num = as.numeric(as.character(age_group)),
    pct = section_total / 4) %>%
  select(-test_total, 
         -child_total, 
         -granny_total) 


ggplot(df.combined, aes(x = age_group, 
                        y = pct, 
                        fill = age_num, 
                        color = age_num)) +
  geom_hline(yintercept = seq(0, 1, 0.25),
             linetype = "solid",
             alpha = 0.1)  +
  geom_hline(yintercept = 0.5, 
             linetype = "dashed") +
  geom_point(position = position_jitterdodge(dodge.width = 0.8,
                                             jitter.width = 0.5,
                                             jitter.height = 0),
             shape = 21,
             size = .8,
             color = "grey30",
             alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(width = 0.8),
               shape = 21, 
               color = "black", 
               size = .7) +
  scale_fill_gradientn(colors = children_palette) +
  scale_color_gradientn(colors = children_palette) +
 scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = str_c(seq(0, 1, 0.25) * 100, "%")) +
  labs(y = "Percentage of choosing \n the person who prevented \n the worse outcome",
       x = "Age (in years)") +
  theme(text = element_text(size = 16),
    axis.text.y = element_text(),
    axis.ticks.y = element_blank(),
    legend.position = "none",
    panel.background = element_rect(fill = "white"),
    strip.text = element_text(size = 11, 
                              face = "bold"),
    strip.text.x = element_text(margin = margin(b = 3, 
                                                t = 3)),
    plot.margin = margin(t = 0.8,
                         l = 0.5, 
                         r = 1, 
                         b = 0.1, 
                         unit = "cm"),
    strip.text.y = element_text()
  ) +
  facet_wrap(~ section, nrow = 1,
             labeller = labeller(section = c(
               "counterfactual"   = "Who should Granny thank? \nExperiment 1",
               "child_preference" = "Which object do you like?",
               "granny_preference"= "Which object does Granny like?"
             )))


ggsave("../../figures/experiment1_appendix/experiment1_appendix.pdf",  width = 10, height = 4)

```

# SESSION INFO
```{r}

sessionInfo()

```